\DndPowerHeader%
    {Adapt Body\label{pwr:adapt_body}}
    {5th-level Prana Bindu}
    {1 action}
    {Self}
    {MB 4, PD 9}
    {Concentration, up to 1 hour}
    {None}
Your body automatically adapts to hostile
environments. You can adapt to underwater, extremely hot,
extremely cold, or airless environments, allowing you to survive
as if you were a creature native to that environment. You
can breathe and move (though penalties to movement and attacks,
if any for a particular environment, remain), and you take
no damage simply from being in that environment. You need
not specify what environment you are adapting to when you
manifest this power; simply activate it, and your body will
instantly adapt to any hostile environment as needed throughout
the duration.

You can somewhat adapt to extreme environmental features such
as acid, lava, fire, and lightning. Any environmental feature
that normally deals damage to you deals
you only half the usual amount of damage.

In any case, you have advantage on Constitution saving throws
to maintain concentration on powers if damage or an otherwise
hazardous effect from the environment you are adapting to
prompted the save.

\DndPowerHeader%
    {Affinity Field\label{pwr:affinity_field}}
    {6th-level Prana Bindu}
    {1 action}
    {Self (20-foot radius)}
    {MB 6, PD 11}
    {Concentration, up to 1 minute}
    {None}
You create an affinity feedback loop with all creatures within a 20-foot
radius surrounding you that fail a Constitution saving throw.
Throughout the power's duration, affected creatures take all damage
as you do and heal all wounds as you do.
Hit points gained or lost persist after this power ends.
In addition, any ability score increase or decrease you incur is passed
onto affected creatures.

If you are affected by a psionic power of 3rd level or lower while this power is active,
creatures with an affinity to you are also affected as if they were the target
or one of the targets.
All psionic effects transferred in this manner cease
at the end of this power's duration.
If you suddenly become immune to a particular effect or power,
the effect or power to which you are immune cannot be transferred
to creatures that have affinity to you.

\DndPowerHeader%
    {Alter Ego\label{pwr:alter_ego}}
    {5th-level Metacreativity}
    {1 action}
    {Self}
    {MB 5, PD 9}
    {12 hours}
    {Mundane matter}
You shape mundane matter in your own likeness, creating a
near-perfect physical copy of yourself.
You then impress a shard of your own awareness into the copy.
The copy is a creature of your own type and inherits your mental statistics,
however its Strength, Dexterity and Constitution are all set to 5.
In addition, the creature's hit point maximum is half yours.
It may manifest any powers you know, except it has half your
mental bandwidth, psionics threshold and psi dice (all rounded up).
It does not inherit any of your spellcasting ability.

The copy is loyal to you and any creatures you designate at the
moment of its creation. However, the creature's alignment is the
diametric opposite of your own. For example, if your own alignment
is lawful good, the copy's alignment is chaotic evil. A neutral in
either of your alignment axes is preserved for the copy;
for example, neutral good becomes neutral evil; true neutral is mapped
to true neutral, etc.
The copy will therefore carry out objectives you designate
as long as those objectives are consistent with their alignment.

The copy persists until the power's duration ends, the copy
is reduced to 0 hit points, or you manifest \nameref{pwr:alter_ego} again,
at which point it returns to the matter from which it was constituted.

\DndPowerHeader%
    {Assimilate\label{pwr:assimilate}}
    {9th-level Prana Bindu}
    {1 action}
    {Touch}
    {MB 10, PD 17}
    {Instantaneous}
    {None}
Your index finger turns black as obsidian.
A creature touched by you is partially assimilated into your form
and takes 20d6 points of damage on a failed Constitution saving throw,
or half as much on a success.
Any creature reduced to 0 or fewer hit points by this power is killed,
entirely assimilated into your form,
leaving behind only a trace of fine dust.
An assimilated creature's equipment is unaffected.

A creature that is partially assimilated into your form
(that is, a creature that has at least 1 hit point
following your use of this power)
grants you a number of temporary hit points equal to
half the damage you dealt for 1 hour.

A creature that is completely assimilated grants you
a number of temporary hit points equal to
the damage you dealt and a
+4 bonus to each of your ability scores for 1 hour.
If the assimilated creature knows psionic powers,
you gain knowledge of one of its powers for 1 hour.
You also gain some semblance of a creature you completely assimilate
for 1 hour, granting you a +10 bonus on Charisma checks in which you
attempt to impersonate that creature during that time.

\DndPowerHeader%
    {Attraction\label{pwr:attraction}}
    {1st-level Voice}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 hour}
    {Speech, Sight}
Your Voice plants a compelling attraction
in the mind of a creature you can see and that can hear
and understand you.
The attraction can be toward a particular person or an object.

The target makes a Wisdom saving throw. If the target fails,
they will take reasonable steps to meet, get close to, attend,
or find the object of its implanted attraction. Otherwise,
the power has no effect.

For the purpose of this power, `reasonable' means that, while
attracted, the target doesn't suffer from blind obsession.
They will act on this attraction only when not engaged in
combat. The target won't perform obviously suicidal actions.
They can still recognize danger but will not flee unless the
threat is immediate.

If you make the target feel an attraction to yourself, you
can't command them indiscriminately, although they will be
willing to listen to you (even if they disagree). Accordingly,
this power grants you advantage on any social skill checks
you make involving the target.
\augment{For every 2 additional psi dice you spend, this power's
save DC increases by 1 and you gain a cumulative +1 bonus
on social skill checks.
}
\DndPowerHeader%
    {Aversion\label{pwr:aversion}}
    {2nd-level Voice}
    {1 action}
    {30 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 hour}
    {Speech, Sight}
Your Voice plants a powerful aversion in
the mind of a creature you can see in range
and that can hear and understand you. If the object
of the implanted aversion is an individual or a physical object,
the target will prefer not to approach within 30 feet of it.
If it is a word, they will try not to utter it; if it is an
action, they will not willingly attempt to perform it; and
if it is an event, they will not willingly attend it. The
subject will take reasonable steps to avoid the object of
its aversion, but will not put themselves in jeopardy by doing
so.

If the subject is forced into taking an action they have an
aversion to, they have disadvantage on any attack rolls, ability
checks, or skill checks involved.
\augment{For every 2 additional psi dice you spend, this power's
save DC increases by 1 and the duration increases by 1 hour.
}
\DndPowerHeader%
    {Banishment, Psionic\label{pwr:banishment_psionic}}
    {4th-level Spacefolding}
    {1 action}
    {120 feet}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {Sight}
You warp space and time,
attempting to force a creature to return back to their
native plane of existence.
The target must succeed on a Charisma saving throw,
otherwise they succumb to the effects described below.

If the target is native to the plane of existence you are on,
they are transported to a pocket dimension just large enough
to encompass their physical size.
The pocket dimension is harmless,
and the target is free to take actions as normal.
The target remains there until the power ends,
in which case they return to the space they previously occupied
before being banished or, if that space is occupied,
the nearest unoccupied space.

If the target is not native to the plane of existence you are on,
the target is shunted through space and returned to its home plane.
The target has a limited degree of control on its homewards journey,
and, if they succeed on another Charisma saving throw,
may choose the rough location of their arrival.
If the power ends before 1 minute has passed,
the target returns in the same way as described in the foregoing paragraph.
Otherwise,
the target does not return.
\augment{For every 3 additional psi dice you spend, you can
target one additional creature.
}
\DndPowerHeader%
    {Bestow Power\label{pwr:bestow_power}}
    {2nd-level Voice}
    {1 action}
    {20 feet}
    {MB 2, PD 3}
    {Instantaneous}
    {Speech, Sight}
You Voice creates a link between your own
mind and that of another psionic creature mind you can see
and that can hear and understand you,
creating a brief conduit through which mental energy can be
shared. When you manifest this power, the subject gains up
to 2 psi dice. You can then transfer psi dice to a subject
on a 1 to 1 basis up to their psionic threshold.

\DndPowerHeader%
    {Biofeedback\label{pwr:biofeedback}}
    {2nd-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {None}
You can toughen your body against wounds,
lessening their impact. For the duration of this power,
all incoming damage from separate sources is reduced by 2.
\augment{For every 3 additional psi dice you spend,the amount
of damage reduced increases by 1.
}
\DndPowerHeader%
    {Bite of the Wolf\label{pwr:bite_of_the_wolf}}
    {1st-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {None}
You temporarily alter your genomic makeup
such that your posture becomes stooped forward, and you grow
a muzzle complete with fangs. You gain one bite attack each
round which can be used as a bonus action or as a replacement
for one of your attacks. Treat the bite as a melee weapon
attack. The bite deals 1d8 piercing damage (assuming you are
a Medium creature) when it hits. Your bite can be affected
by powers, spells, and effects that enhance or improve weapons.

If you are not a Medium creature, your bite attack's base
damage varies as follows: Tiny 1d4; Small 1d6; Large 2d6;
Huge 2d8; Gargantuan 4d6.

Based on your psi knight level, your bite increases in ferocity
as noted here: at 5th level your bite deals an extra 1d8 points
of damage, at 10th level an extra 2d8, at 15th level an extra
3d8, and at 20th level an extra 4d8 points.

\DndPowerHeader%
    {Blow Up Object With Mind\label{pwr:blow_up_object_with_mind}}
    {1st-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 1, PD 1}
    {Instantaneous}
    {Sight}
Your terrifying mental ability can cause
matter to wrench itself apart. Choose a non-magic nor non-psionic
object within range that you can see.
The object can be carried or worn by a
creature. Make a psionics attack roll against the object.
The AC is determined by the size of object, shown below.

\begin{table}[htbp]%
    \begin{DndTable}[
        width=\columnwidth,
        header=Object AC and Damage
    ]{X c c}
        Size & AC & Damage Die \\
Tiny (bottle, pancakes) & 11 & 2d6 \\
Small (chest, lute, sword) & 13 & 2d8 \\
Medium (barrel, chandelier) & 15 & 2d10 \\
Large (cart, 10x10 ft. window) & 17 & 2d12 \\
    \end{DndTable}
\end{table}

If the attack hits,
the object explodes. Any creature within 10 feet of the
object must make a Dexterity saving throw. If they fail,
they take bludgeoning damage equal to the damage shown in
the table below, as dependent on the object's size.
Otherwise, they take half that amount of damage.
If the object was being worn or carried by a creature,
that creature has disadvantage on the saving throw.
\augment{For every 2 additional psi dice you spend, roll one
extra die using the same damage die as given for the object's
size.
}
\DndPowerHeader%
    {Body Equilibrium\label{pwr:body_equilibrium}}
    {2nd-level Prana Bindu}
    {1 action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 10 minutes}
    {None}
You can adjust your body's equilibrium to
correspond with any solid or liquid that you stand on. Thus,
you can walk on water, quicksand, or even a spider's web
without sinking or breaking through (this effect does not
confer any resistance to particularly sticky webs). You can
move at your normal speed, but you cannot take the Dash action
on an non-firm surface without sinking or breaking through.

If you fall from any height while using this power, damage
from the impact is halved.

\DndPowerHeader%
    {Bolt\label{pwr:bolt}}
    {1st-level Metacreativity}
    {1 action}
    {Touch}
    {MB 1, PD 1}
    {Concentration, up to 1 hour}
    {Mundane matter}
You create 2d4 crossbow bolts, arrows or
sling bullets. The ammunition dissipates upon hitting a target
or when the power ends. The ammunition has a +1 bonus to attack
and damage rolls.
\augment{For every 4 additional psi dice you spend, this power
improves the ammunition's bonus to attack and damage rolls
by +1, up to a maximum of three for each.
}
\DndPowerHeader%
    {Boots of the Demon King\label{pwr:boots_of_the_demon_king}}
    {1st-level Prana Bindu}
    {1 attack when you take the Attack action}
    {Self (5-foot radius)}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
Your legs briefly gain incredible strength,
and your boots crackle with lightning. Whenever you take the Attack
action, you can manifest this power any time during that action
to replace one of your attacks with a special unarmed
kick taken against an opponent within your melee range. If the
attack hits, the target takes damage from your unarmed strike
as normal plus 2d4 lightning damage. If the target is above
half their hit point maximum, they must succeed on a Strength
saving throw or be knocked prone. If the target is below half
their hit point maximum, they must succeed on a Strength saving
throw or immediately be sent a distance into the air equal
to your Strength score. They then fall prone and take fall
damage as normal.
\augment{For every additional psi die you spend, the lightning
damage dealt by this power increases by 1d4.
}
\DndPowerHeader%
    {Breath of Numinex\label{pwr:breath_of_numinex}}
    {6th-level Prana Bindu}
    {1 action}
    {Self (30-foot cone)}
    {MB 5, PD 11}
    {Instantaneous}
    {None}
Your alter your body's chemistry in an instant,
allowing you to secrete a vitriolic acid which you spew forth
in a 30-foot cone centred on yourself. All creatures inside
the cone must make a Dexterity saving throw, taking 11d6 acid
damage on a failed save or half as much on a successful save.
\augment{For every additional psi dice you spend, this power's
damage increases by 1d6.
}
\DndPowerHeader%
    {Burst\label{pwr:burst}}
    {1st-level Prana Bindu}
    {Free action, see text}
    {Self}
    {MB 1, PD 1}
    {Until the end of your turn}
    {None}
You subtly alter the space between matter
to gain a quick boost to your perceived speed. At any point
in your turn, you may use a free action to manifest this power
and gain an extra 10 feet of base movement speed for that
turn only.

\DndPowerHeader%
    {Chameleon\label{pwr:chameleon}}
    {1st-level Prana Bindu}
    {1 action}
    {Self}
    {MB 1, PD 1}
    {Concentration, up to 1 hour}
    {None}
Your skin and equipment take on the color
and texture of nearby objects, including floors and walls.
You gain the ability to hide in dim light while the power
lasts. You may also attempt to hide in normal levels of illumination,
however your Dexterity (Stealth) check has disadvantage.

\DndPowerHeader%
    {Cloud Mind\label{pwr:cloud_mind}}
    {2nd-level Voice}
    {1 action}
    {30 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {Sight}
Your make yourself completely undetectable
to a target you can see by erasing all awareness of your presence
from its mind. If the target fails a Wisdom saving throw,
this power has the following effects.

First, you are invisible and inaudible to the creature. It
cannot even detect your presence by means of blindsight, scent,
or tremorsense. It cannot pinpoint your location by any means.
\textit{Exception:} Creatures with truesight are still able
to discern your location, and therefore the power has no effect
on them.

Second, the target remains unaware of your actions, provided
you do not make any attacks or cause any obvious or directly
threatening changes in the target's environment. If you
attack the target, the power ends.

If you take an action that creates a sustained and obvious
change in the target's environment---for example, attacking
a creature aside from the target or moving a large or attended
object the target can see---the target immediately repeats
the saving throw against the power. An ally of the target
creature that is able to see or perceive you can warn the
target and thereby grant it another saving throw.

\DndPowerHeader%
    {Cloud Mind, Mass\label{pwr:cloud_mind_mass}}
    {6th-level Voice}
    {1 action}
    {30 feet}
    {MB 6, PD 11}
    {Concentration, up to 1 minute}
    {None}
As the \power{cloud mind} power, except as
noted here. Each creature within a 30-foot radius is affected
individually.

\DndPowerHeader%
    {Compel\label{pwr:compel}}
    {4th-level Voice}
    {1 action}
    {60 feet}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {Speech, Sight}
Your Voice compels a creature to act according
to your wishes. Choose a creature within range that you can see
and that can hear and understand you.
You then suggest a course of activity
limited to no more than five words that that creature is to
take. The course of action can be harmful to the creature
or contrary to its intentions.

The target must make a Wisdom saving throw. The target has
advantage on the saving throw if the course of action is plainly
harmful or against the creature's wishes. If the target fails,
it pursues the course of action to the best of its ability.
The compelled course of action can continue for the entire
duration of the power. If the compelled activity can be completed
in a shorter time, the power ends when the target finishes
what it was asked to do.

You can also specify conditions that will trigger a special
activity during the duration. For example, you might suggest
that a knight give her warhorse to the first beggar she meets.
If the condition isn't met before the power expires, the
activity isn't performed.

\DndPowerHeader%
    {Conceal Thoughts\label{pwr:conceal_thoughts}}
    {1st-level Voice}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 hour}
    {Sight}
Choose a target within range that you can
see. You protect the target's thoughts from analysis. While
the duration lasts, the target gains advantage on 
Charisma (Deception) checks against those
attempting to discern their true intentions
with Wisdom (Insight). They also gain advantage on saving
throws against any power or spell used to read their mind
(such as detect thoughts).

\DndPowerHeader%
    {Concealing Membrane\label{pwr:concealing_membrane}}
    {2nd-level Metacreativity}
    {1 action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {Mundane matter}
You weave a quasi-real membrane around yourself,
which makes you lightly obscured. You remain visible within
the translucent, amorphous enclosure. This distortion also
grants you half cover thanks to the rippling membrane encasing
your form. You can pick up or drop objects, easily reaching
through the film. Anything you hold is enveloped by the membrane.
Likewise, you can engage in melee, make ranged attacks, and
manifest powers without hindrance.

\DndPowerHeader%
    {Confusion, Psionic\label{pwr:confusion_psionic}}
    {3rd-level Voice}
    {1 action}
    {90 feet}
    {MB 3, PD 5}
    {Concentration, up to 1 minute}
    {Speech, Sight}
Your Voice berates and beleaguers the mind of another creature,
rendering them dazed and confused.
Choose a creature you can see within range that can
hear and understand you.
That creature must succeed on a Wisdom saving throw or
be affected by this power.

An affected creature cannot take reactions.
While the power lasts,
at the start of each of that creature's turns
you hone your Voice in such a way
so as to coarsely influence the actions of the affected creature.
Roll a d6. If the result is 1--5,
choose freely from the table below
to determine the quality of your Voice
and the associated effect on the creature for that turn.
The creature cannot do anything on that turn except for
the relevant effect given above.
If the result is a 6, the creature is unaffected by your Voice
and acts normally (but is still affected by the power).

\begin{table}[htbp]%
    \begin{DndTable}[
        width=\columnwidth,
        header=Psionic Confusion Effects
    ]{l X}
        Voice Quality & Effect \\
Grating & The target takes 2d10 psychic damage \\
Booming & The target is deafened \\
Discordant & The target uses all their movement to move in a random direction (determined by the roll of a d8) \\
Frenetic & The target makes a single melee attack against a randomly determined creature in their reach, if possible \\
Pacifying & The target does nothing \\
    \end{DndTable}
\end{table}

At the end of an affected creature's turns,
they may repeat the Wisdom saving throw,
ending the power on a success.
\augment{For every 3 additional psi dice you spend, this power's
save DC increases by 1, and the power can affect an additional
target. Any additional target cannot be more than 10 feet
from another target of the power.
}
\DndPowerHeader%
    {Control Air\label{pwr:control_air}}
    {2nd-level Psychokinesis}
    {1 action}
    {120 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {Sight}
You have some control over wind speed and
direction. The speed of the wind in empty spaces you can see
within 120 feet of you can
be increased or decreased by up to 10 knots. This power also
gives you the ability to alter the direction of the wind by
as much as 90 degrees.

Powerful enough winds can cause creatures to be knocked prone.
Creatures of size Small or smaller that are subject to winds
between 25--45 knots must succeed on a DC 10 Strength saving
throw or be knocked prone. If they wind speed is greater than
45 knots, this applies to Medium creatures as well (DC 10),
and the DC for size Small or smaller increases by 5.
\augment{For every additional psi die you spend, you
can modify the wind speed by an additional 10 knots,
to a maximum change in wind speed of 50 knots.
}
\DndPowerHeader%
    {Control Body\label{pwr:control_body}}
    {4th-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {Sight}
You psychokinetically control the actions
of any humanoid (including undead or outsiders with a humanoid
physiology) that you can see within range. The target immediately
makes a Strength saving throw, with the power ending if they
succeed and continuing if they fail. Control body doesn't
require mental contact with the target, since you are actually
forcing limb movements independent of the target's mind.
You can force the target to stand up, sit down, walk, turn
around, and so on, but operating the vocal cords is too difficult.
You can also hold the target immobile, rendering it paralysed.
You cannot force the target to manifest powers, cast spells,
or use any special ability that is not a function of just
its body movements. If you lose sight of the target, the effect
of this power ends.

If you force the target to engage in combat, its attack bonus
is equal to your psionics attack bonus, and its bonus on damage
rolls is equal to your psionics ability modifier.
A creature subject to this power cannot take reactions.
The target gains no benefit to its AC from its Dexterity,
but it does gain a bonus to
its AC equal to your Intelligence bonus.

Although the subject's body is under your control, the subject's
mind is not. Creatures capable of taking purely mental actions
(such as manifesting powers) can do so.
\augment{For every 2 additional psi dice you spend, this power
can affect a target one size category larger.
}
\DndPowerHeader%
    {Control Sound\label{pwr:control_sound}}
    {2nd-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {None}
You shape and alter existing sounds. You
can target one sound, such as a person speaking or singing,
or a group of related sounds, such as the patter of many raindrops
or the tramp of soldiers passing by. A sound as quiet as a
snapping finger can be controlled. You can substitute any
sound you have heard for the target sound. If you attempt
to exactly duplicate the voice of a specific individual, or
an inherently terrifying sound (such as a dragon's roar),
you must succeed on a Deception check
(with underlying ability determined by your psionics ability)
opposed by the intended listener's Wisdom (Insight) check
to avoid arousing suspicion.

You can entirely muffle a noise or magnify a sound to such
loudness that it drowns out all other conversation in the
immediate area.

Alternatively, you can use up the power in an instant. You
do this by modulating a sound into a one-time destructive
impetus that shatters nonmagical/nonpsionic unattended objects
of crystal, glass, ceramic, or porcelain make in the area
(e.g. vials, bottles, flasks, jugs, mirrors, and so forth).

\DndPowerHeader%
    {Correspond\label{pwr:correspond}}
    {4th-level Voice}
    {10 minutes}
    {Unlimited, see text}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {None}
You forge a mental link with a creature with
which you have previously had physical or mental contact and
that has an Intelligence score of 5 or greater.
The target need not be on the same plane of existence as you.
The target recognises you, and you can mentally
communicate with it for
the duration (though nothing forces the subject to respond
to you), exchanging messages of twenty-five words or less
once per round.

\DndPowerHeader%
    {Counterpower\label{pwr:counterpower}}
    {3rd-level Prescience}
    {1 reaction, which you take when you see a creature
within 60 feet of you manifesting a power
}
    {60 feet}
    {MB 3, PD 5}
    {Instantaneous}
    {Sight}
You briefly peer into a future where another creature
has manifested a power. Armed with this uncanny insight,
you attempt to interrupt a creature in the process of
manifesting that power, preventing that future from actualising.
If the creature is manifesting a power
of 3rd level or lower, its power fails and has no effect.
If it is manifesting a power of 4th level or higher,
make an ability check using your psionics ability.
The DC equals 10 + the power's level, as usual taking into account
whether or not the power you are reacting to has been augmented.
On a success, the creature's power fails and has no effect.
\augment{For every 4 psi dice you spend,
the base level (3) at which a power is automatically interrupted
increases by one.
}
\DndPowerHeader%
    {Create Armour With Mind\label{pwr:create_armour_with_mind}}
    {1st-level Metacreativity}
    {1 action}
    {Touch}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Mundane matter}
You touch any mundane matter in front of
you, morphing it into armour of your choosing from the armour
table (phb 144). The armour is made of ordinary materials
as appropriate for its kind, and you can mould it around your person
such that it is immediately donned.
If you lose contact with the armour you created for 2
or more consecutive rounds, it loses its coherence and returns
to the substance(s) it originated as.
\augment{You can augment this power in one or both of the following ways.
  \begin{itemize}
    \item For every 6 additional psi dice you spend,
      this power adds a +1 bonus to the armour's AC (to a maximum of +3).
    \item If you spend 8 psi dice,
      the armour gains power resistance equal to your psionics save DC.
  \end{itemize}}
\DndPowerHeader%
    {Create Object With Mind\label{pwr:create_object_with_mind}}
    {5th-level Metacreativity}
    {1 minute}
    {30 feet}
    {MB 4, PD 9}
    {See text}
    {Mundane matter}
As the \spell{creation} spell, except as
noted here.
\augment{For every 3 additional psi dice you spend, the cube's
size increases by 5 feet.
}
\DndPowerHeader%
    {Create Sound\label{pwr:create_sound}}
    {1st-level Metacreativity}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {None}
You create a volume of sound that rises,
recedes, approaches, or remains at a fixed place centred at
a point within range. You choose what type of sound the power
creates when manifesting it and cannot thereafter change its
basic character. The volume of sound created, however, depends
on your psionic threshold. You can produce as much noise as
four normal humans per psionic threshold (maximum of twenty humans).
Thus, talking, singing, shouting, walking, marching, or running
sounds can be created. The noise produced can be virtually
any type of sound within the volume limit. A horde of rats
running and squeaking is about the same volume as eight humans
running and shouting. A roaring lion is equal to the noise
from sixteen humans, while a roaring dire lion is equal to
the noise from twenty humans.

If you wish to create a specific message, up to twenty-five
words can be created, and those words repeat
until the duration expires or the power is dismissed. If you
attempt to exactly duplicate the voice of a specific individual
or an inherently terrifying sound (such as a dragon's roar),
you must succeed on a Deception check
(with underlying ability determined by your psionics ability)
opposed by the listener's
Wisdom (Insight) check to avoid arousing suspicion.

Create sound can be used to bring sounds into existence that
you later manipulate by manifesting \power{control sound}.

\DndPowerHeader%
    {Create Weapon With Mind\label{pwr:create_weapon_with_mind}}
    {1st-level Metacreativity}
    {1 action}
    {Touch}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Mundane matter}
You touch any mundane matter in front of
you, morphing it into a weapon of your choosing from the weapons
table (phb 146). The weapon is made of ordinary materials
as appropriate for its kind. If you choose a projectile weapon,
it comes with 3d6 pieces of ammunition of the applicable type.
If you relinquish your grip on the weapon you called for 2
or more consecutive rounds, it loses its coherence and returns
to the substance(s) it originated as.
\augment{You can augment this power in one or both of the following ways.
  \begin{itemize}
    \item For every 4 additional psi dice you spend,
      this power adds a +1 bonus to the weapon's
      attack and damage rolls (to a maximum of +3).
    \item If you spend 3 psi dice,
      the weapon overcomes a creature's
      resistance to non-magical weapons.
  \end{itemize}
}
\DndPowerHeader%
    {Crisis of Breath\label{pwr:crisis_of_breath}}
    {3rd-level Voice}
    {1 action}
    {120 feet}
    {MB 4, PD 5}
    {Concentration, up to 1 minute}
    {Speech, Sight}
Your Voice compels a humanoid creature you
can see in range
and that can hear and understand you
to purge its entire store of air in one explosive
exhalation, thereby disrupting its autonomic breathing
cycle. The target's lungs do not automatically function again
while the powers's duration lasts.

If the target succeeds on a Wisdom save when crisis of breath
is manifested, it is unaffected by this power. If it fails
its Wisdom save, it can still continue to breathe by taking
a standard action in each round to gasp for breath.

An affected creature can attempt to take actions normally
(instead of consciously controlling its breathing), but each
round it does so, beginning in the round when it failed its
Wisdom save, the target risks blacking out from lack of oxygen.
It must succeed on a Constitution save at the end of any of
its turns in which it did not consciously take a breath. The
DC of this save increases by 1 in every consecutive round
after the first one that goes by without a breath; the DC
drops back to its original value if the target spends an action
to take a breath.

If a target fails its Constitution save, it becomes unconscious.
At the end of its next turn, it drops to 0 hit points but
must take death saving throws. Curing powers or spells can
revive a dying subject normally, so long as this power's
duration has expired.
If the power is still in effect, a revived
creature still must take Constitution saves in each round
when it does not consciously breathe.
\augment{You can augment this power in one or more of the following ways.
\begin{itemize}
  \item If you spend 6 additional psi dice,
        this power can affect up to four creatures
        all within a 20-foot radius.
  \item If you spend 4 additional psi dice,
        this power can also affect creatures other than a humanoid,
        assuming they have a aerobic respiratory system to disrupt.
\end{itemize}
}
\DndPowerHeader%
    {Cushion Fall\label{pwr:cushion_fall}}
    {1st-level Spacefolding}
    {1 reaction, which you take when you suffer any fall damage}
    {Self}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
You recover instantly from a fall and can
absorb some damage from falling. You land on your feet no
matter how far you fall, and you take damage as if the fall
were 10 feet shorter than it actually is. This power affects
you and anything you carry or hold (up to your maximum load).
\augment{For every additional psi die you spend, the power reduces
your damage as if the fall were an additional 10 feet shorter.
}
\DndPowerHeader%
    {Danger Sense\label{pwr:danger_sense}}
    {3rd-level Prescience}
    {1 action}
    {Self}
    {MB 3, PD 5}
    {Concentration, up to 1 hour}
    {None}
You can sense the presence of danger before
your senses would normally allow it. Your intuitive sense
alerts you to danger from traps, giving you advantage on Dexterity
saving throws to avoid traps and a +4 bonus to your AC when
targetted by any attack made by a trap.

\DndPowerHeader%
    {Deceleration\label{pwr:deceleration}}
    {1st-level Spacefolding}
    {1 action}
    {60 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Sight}
You warp space around a creature in range
that you can see, hindering the target's ability to move.
The target must succeed on a Wisdom saving throw, otherwise
their speed (in every movement mode they possess) is halved.

A subsequent manifestation of deceleration on the target does
not further decrease its speed.
\augment{For every 2 additional psi dice you spend, this power
can affect a target one size category larger.
}
\DndPowerHeader%
    {Demoralise\label{pwr:demoralise}}
    {1st-level Voice}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Sight}
Choose 3 hostile creatures that you can see
within range. Each creature must make a Wisdom saving throw.
If they fail, they target takes a 1d4 penalty to attack rolls
and saving throws until the power ends.
\augment{For every two additional psi dice you spend, you
may target one additional creature.
}
\DndPowerHeader%
    {Destiny Dissonance\label{pwr:destiny_dissonance}}
    {1st-level Prescience}
    {1 action}
    {Touch}
    {MB 1, PD 1}
    {1 round per psionic threshold}
    {None}
Your mere touch grants a creature a vision
of the limitless potential of the not-yet-determined future,
possibilities undulating like a cloth blowing in the wind.
Unaccustomed to such a revelation, the creature's mind is
overwhelmed. Make a melee psionics attack against a creature.
If the attack hits, the creature takes 1d10 psychic damage
and becomes poisoned for a number of rounds equal to your
psionic threshold (concluding at the end of their turn
in the final round).
\augment{For every two additional psi dice you spend, this
power's damage increases by 1d8.
}
\DndPowerHeader%
    {Detect Hostile Intent\label{pwr:detect_hostile_intent}}
    {2nd-level Voice}
    {1 action}
    {30 feet}
    {MB 2, PD 3}
    {Concentration, up to 10 minutes}
    {None}
While the duration of this power lasts, you
become aware of the presence of any creatures with hostile
intent within 30 feet of you, and their direction from you
(but not their specific location). The power detects active
aggression, as opposed to vigilance. In addition, while this
power is active you cannot be surprised by creatures that
are susceptible to this mind-affecting power.

While under the effect of this power, you can make Wisdom
(Insight) checks as a free action against anyone you can see
within 30 feet of you.

The power can penetrate barriers, but 3 feet of stone, 3 inches
of common metal, 1 inch of lead, or 6 feet of wood or dirt
blocks it.

\DndPowerHeader%
    {Detect Prying Eyes\label{pwr:detect_prying_eyes}}
    {4th-level Prescience}
    {1 action}
    {40 feet}
    {MB 3, PD 7}
    {One day}
    {None}
You immediately become aware of any attempt
to observe you by means of a Prescience power or Divination
spell. The power's effect radiates in a 40-foot radius from
you and moves as you move. You know the location of every
psionic or magical sensor within the power's area.

If the viewing attempt originates within the area, you also
know the viewer's location. Otherwise, you and the remote
viewer immediately make opposed checks. You make an ability
check using your psionics ability modifier, and the remote
viewer makes a check using their modifier for manifesting
powers or casting spells if a power or spell respectively
gave rise to the remote viewing. If you at least match the
remote viewer's result, you get a visual image of the remote
viewer and a roughly accurate sense of the remote viewer's
direction and distance from you.
If the viewer is on a different plane of existence,
you merely learn which plane the remote viewing attempt is
originating from.

\DndPowerHeader%
    {Detect Psionics\label{pwr:detect_psionics}}
    {1st-level Prescience}
    {1 action}
    {Self}
    {MB 1, PD 1}
    {Concentration, up to 10 minutes}
    {None}
For the power's duration, you sense the
presence of psionics within 30 feet of you. If you sense psionics
in this way, you can use your action to see a faint aura around
any visible creature or object in the area that bears psionic
effects, and you learn the discipline of the effect, if any.

The power can penetrate most barriers, but is blocked by 1
foot of stone, 1 inch of common metal, a thin sheet of lead,
or 3 feet of wood or dirt.

\DndPowerHeader%
    {Detect Thoughts, Psionic\label{pwr:detect_thoughts_psionic}}
    {2nd-level Voice}
    {1 action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {Sight, see text}
Your inner Voice peers into the minds of others,
gleaning information otherwise concealed to you.
When you manifest this power,
and as an action on each turn until the power end,
you can focus on any one creature you can see within 30 feet of you.
If the creature has an Intelligence of 3 or lower,
they are unaffected.

While focusing on a creature,
if the creature has an Intelligence of 14 or higher,
the sensation of a presence within their mind grows on them.
Nonetheless,
you learn the surface level thoughts of that creature.
`Surface level thoughts' includes what is most
immediately on the creature's mind,
however does not include information a creature is attempting to conceal
unless they are careless or recklessly indifferent
towards revealing that information.

As an action,
you can probe deeper into the creature's mind,
in which case the creature must make a Wisdom saving throw.
If they fail,
you gain insight into one of its more inner desires,
including something that looms large in its mind.
You may then use another action to glean another piece of information
from the creature, prompting a further save.
If they succeed the original save, the power ends.
Regardless,
the creature knows that you are probing into its mind
and can use an action on its turn to make an Intelligence check
contested by a check using your psionics ability modifier.
If the creature succeeds on the contest,
the power ends.

You can also use this power to detect the presence of thinking creatures
you can't see.
When you manifest the power or as your action during the duration,
you can search for thoughts within 30 feet of you.
The power can penetrate barriers,
but 2 feet of rock, 2 inches of any metal other than lead,
or a thin sheet of lead blocks you.
You can't detect a creature with an Intelligence of 3 or lower.
Once you detect the presence of a creature in this way,
you can read its thoughts for the rest of the duration as described above,
even if you can't see it, but it must still be within range.

\DndPowerHeader%
    {Diamond Bullet\label{pwr:diamond_bullet}}
    {1st-level Metacreativity}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Instantaneous}
    {Sight, Line of Effect, Mundane matter}
Upon manifesting this power, you propel a
diamond bullet at a target within range that you can see and
that you have line of effect to. Make a ranged psionics attack
against the target. On a hit, the bullet deals 1d6 points
of piercing damage.
\augment{For every 2 additional psi dice you spend, this power's
damage increases by 2d6.
}
\DndPowerHeader%
    {Dimension Swap\label{pwr:dimension_swap}}
    {2nd-level Spacefolding}
    {1 action}
    {60 feet}
    {MB 2, PD 3}
    {Instantaneous}
    {Sight}
You instantly swap positions between your
current position and that of a designated ally in range that
you can see. Alternatively, you can swap the positions of
any two allies you can see that are both in range. This power
affects creatures of Large or smaller size. You can bring
along objects, but not other creatures.
\augment{For every 2 additional psi dice you spend, this power
can affect a target one size category larger.
}
\DndPowerHeader%
    {Dispel Psionics\label{pwr:dispel_psionics}}
    {3rd-level Psychokinesis}
    {1 action}
    {120 feet}
    {MB 3, PD 5}
    {Instantaneous}
    {None}
Choose one creature, object, or psionic effect
within range. Any power of 3rd level or lower on the target
ends. For each power of 4th level or higher on the target,
make an ability check using your psionics ability. The DC
equals 10 + the power's level. On a successful check, the
power ends.
\augment{For every 2 additional psi dice you spend, you automatically
end the effects of a power on the target that is one level
higher.
}
\DndPowerHeader%
    {Dissipating Touch\label{pwr:dissipating_touch}}
    {1st-level Spacefolding}
    {1 action}
    {Touch}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
Your mere touch can disperse the surface
material of a foe or object, sending a tiny portion of it
far away. This effect is disruptive; thus, your successful
melee psionics attack deals 3d6 points of force damage.
\augment{For every additional psi dice you spend, this power's
damage increases by 1d6.
}
\DndPowerHeader%
    {Dissolving Touch\label{pwr:dissolving_touch}}
    {2nd-level Prana Bindu}
    {1 bonus action}
    {Touch}
    {MB 2, PD 3}
    {1 minute}
    {None}
Your touch, claw, or bite is corrosive, and
sizzling moisture visibly oozes from your natural weapon or
hand. You deal 4d6 acid damage to any creature or object you
hit with your next melee attack using the coated natural weapon
or unarmed attack. You are immune to your own acid. If you
do not land a hit within a minute of manifesting this power,
the effect wears off.
\augment{For every 2 additional psi dice you spend, this power's damage increases by 1d6.}
\DndPowerHeader%
    {Distant Gaze\label{pwr:distant_gaze}}
    {2nd-level Prescience}
    {1 action}
    {See text}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {None}
You can see and hear a distant location almost
as if you were there. You don't need to see the location,
but the locale must be known; that is, it must be a place
familiar to you or an obvious one proximate to you, such as
behind a nearby door, around a nearby corner, or in a grove
of nearby trees.
The location cannot be more than one mile from you.
Once you have selected the locale, the focus
of your clairvoyant sense doesn't move, but you can rotate
it in all directions to view the area as desired. Unlike other
scrying powers, this power does not allow psionically
or supernaturally enhanced senses to work through it.

If the chosen locale is magically or psionically dark, you
see nothing. If it is naturally pitch black, you can see in
a 10-foot radius around the center of the power's effect.
The power does not work across planes.

\DndPowerHeader%
    {Distract\label{pwr:distract}}
    {1st-level Voice}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Sight}
You cause the mind of a creature
you can see in range to wander, distracting them. If the target
fails a Wisdom saving throw, they have disadvantage on all
Wisdom (Perception) and Wisdom (Insight) checks until the
power ends.

\DndPowerHeader%
    {Divert Teleport\label{pwr:divert_teleport}}
    {7th-level Spacefolding}
    {1 reaction, when you take whenever another creature teleports}
    {120 feet}
    {MB 6, PD 13}
    {Concentration, up to 10 minutes}
    {Sight}
You can bend space and time to divert the
final destination of any teleportation attempt made by any
creature within 120 feet of you that you can see.
This power is manifested as a reaction to that attempt.
You can divert the destination of both incoming and outgoing
teleportations whether psionic and magical in nature. Whenever you use this
power, the teleporting creature makes a Wisdom saving throw.
If they fail, the teleport is diverted; otherwise, the teleportation
proceeds as normal.

This power affects creatures whose teleportation is contingent
on the target's magic or psionics, for example the willing creature
optionally brought along by use of the spell \spell{dimension door}.
That is to say, any number of secondary creatures
who teleport because of the action of the target are also diverted.  

For the purpose of this power, `divert' means you choose
the actual destination of any teleportation attempt you can
affect, as if you yourself were teleporting to that location,
regardless of the teleportation range of the effect you are
diverting. The destination you choose must be a location with
which you are very familiar by experience or that you have
studied carefully.

\DndPowerHeader%
    {Drain Power\label{pwr:drain_power}}
    {4th-level Voice}
    {1 action}
    {30 feet}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {Speech, Sight}
Your Voice commands a target to relinquish
their psionic power reserves to you. Choose a target that
you can see within range
and that can hear and understand you.
The target must succeed on a Wisdom
saving throw or immediately lose 1d6 psi dice, one of which
is added to your pool of psi dice. If the target has innate
talents, you may instead nominate to expend one use of any
of their innate talents which,
if manifested as a power,
would have a psi dice cost of up to 6.

The target continues to lose 1d6 psi dice each round you maintain
concentration on the power and the subject remains in range
(or, alternatively, continues to expend uses of innate talents
that you choose). In addition, you must continually use your
action on your turn to use the power. If the subject is left
with 0 psi dice or has totally expended their uses of innate
talents, the power ends.

\DndPowerHeader%
    {Duplicate Power\label{pwr:duplicate_power}}
    {8th-level Prescience}
    {1 action}
    {See text}
    {MB 6, PD 15}
    {See text}
    {See text}
Duplicate Power lets you replicate many types of psionic effects,
allowing you to do any of the following:
\begin{itemize}
  \item Duplicate any psion power of 6th level or lower,
        provided the power is not on a discipline sublist unavailable to you.
  \item Duplicate any other power of 5th level or lower,
        provided the power is not on a discipline sublist unavailable to you.
  \item Duplicate any psion power of 5th level or lower,
        even if it's on a discpline sublist unavailable to you.
  \item Combine the effects of any two powers known to you
        as long as sum of the two powers' levels is less than or equal to 8.
\end{itemize}
A duplicated power allows saving throws as normal, and has the same
duration, requirements, range, etc. as the original power.
If the original power specifies concentration as a requirement,
that also applies when replicated with Duplicate Power.
If you have replicated the effects of two powers with different requirements,
the more restrictive requirement applies.
For example, when combining two powers with a 60 ft. and 30 ft. range,
the 30 ft. range applies for the overall combined effect produced with Duplicate Power. 

\DndPowerHeader%
    {Déjà Vu\label{pwr:déjà_vu}}
    {1st-level Voice}
    {1 action}
    {60 feet}
    {MB 1, PD 1}
    {1 round}
    {Speech, Sight}
The power of your Voice commands a target
in range that you can see to repeat their previous decisions.
The target must be able to hear and understand you.
The target must succeed on a Wisdom saving throw or be forced
to repeat the actions they took on their previous turn. If
the situation has changed in such a way that the target can't
take the same actions again (if its foe is dead, or the target
has run out of psi dice, and so on), the target stands still
and takes no actions for 1 round. In any event, the target
can still defend itself.
\augment{For every 2 additional psi dice you spend, this power'ssave
DC increases by 1.
}
\DndPowerHeader%
    {Empath's Understanding\label{pwr:empaths_understanding}}
    {1st-level Voice}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Sight}
You detect the surface emotions of a creature
you can see in range. You can sense basic needs, drives, and
emotions. Thirst, hunger, fear, fatigue, pain, rage, hatred,
uncertainty, curiosity, friendliness, and many other kinds
of sensations and moods can all be perceived.

You gain a +2 bonus to any social skill check involving the
target that you make in the round when you cease concentrating
on this power.
\augment{You can augment this power in one or both of the
following ways.
\begin{itemize}
  \item For every additional psi die you spend,
  this power's range increases by 5 feet.
  \item If you spend 2 additional psi dice, this power's
  maximum duration increases to 1 hour.
\end{itemize}
}
\DndPowerHeader%
    {Empathic Feedback\label{pwr:empathic_feedback}}
    {4th-level Voice}
    {1 action}
    {Self}
    {MB 3, PD 7}
    {Concentration, up to 10 minutes}
    {Speech}
Your Voice berates your attacker, causing
it to empathically share your pain and suffering. Each time
a creature that can hear and understand you hits you,
it takes damage equal to the amount it
dealt to you or 5 points, whichever is less. This damage is
empathic in nature, so powers and abilities the attacker may
have such as damage reduction and regeneration do not lessen
or change this damage. The damage from empathic feedback has
no type, so even if you took fire damage from a creature that
has immunity to fire, empathic feedback will damage your attacker.
\augment{For every additional psi die you spend, this power's
damage floor (base of 5) increases by 1.
}
\DndPowerHeader%
    {Energy Bolt\label{pwr:energy_bolt}}
    {3rd-level Psychokinesis}
    {1 action}
    {Self (120-foot line)}
    {MB 3, PD 5}
    {Instantaneous}
    {Line of Effect}
Upon manifesting this power, you choose cold,
lightning, fire, or thunder. You release a powerful stroke
of energy of the chosen type that emanates from your finger
tips, forming a line 120 feet long and 5 feet wide. Each creature
in the line must make a Dexterity saving throw. A creature
takes 6d6 points of damage of the chosen type on a failed
save, or half as much on a successful save.

\subparagraph{Cold} A bolt of this energy type deals +1 point
of damage per die. The saving throw to reduce damage from
a cold bolt is a Constitution save instead of a Dexterity
save.

\subparagraph{Lightning} Manifesting a bolt of this energy
type provides a +2 bonus to the save DC if the target is wearing
metal armour.

\subparagraph{Fire} A bolt of this energy type deals +1 point
of damage per die.

\paragraph{Thunder} A bolt of this energy type deals -1 point
of damage per die but provides a +1 bonus to the save DC.
\augment{For every additional psi die you spend, this power's
damage increases by one die (d6). For every additional two dice
of damage, this power's save DC increases by 1.
}
\DndPowerHeader%
    {Energy Burst\label{pwr:energy_burst}}
    {3rd-level Psychokinesis}
    {1 action}
    {Self (30-foot sphere)}
    {MB 3, PD 5}
    {Instantaneous}
    {Line of Effect}
Upon manifesting this power, you choose cold,
lightning, fire, or thunder. You create an explosion of unstable
energy of the chosen type that radiates over a 30-foot sphere
centred on yourself. Every creature or object within range
that fails a Dexterity saving throw takes 6d6 damage of the
chosen type, or half as much damage on a successful save.
The explosion creates almost no pressure. Since this power
extends outward from you, you are not affected by the damage.

\subparagraph{Cold} A burst of this energy type deals +1 point
of damage per die. The saving throw to reduce damage from
a cold burst is a Constitution save instead of a Dexterity
save.

\subparagraph{Lightning} Manifesting a burst of this energy
type provides a +2 bonus to the save DC to creatures wearing
metal armour.

\subparagraph{Fire} A burst of this energy type deals +1 point
of damage per die.

\subparagraph{Thunder} A burst of this energy type deals -1
point of damage per die but provides a +1 bonus to the save
DC.
\augment{For every additional psi die you spend, this power's
damage increases by one die (d6). For each extra two dice
of damage, this power's save DC increases by 1.
}
\DndPowerHeader%
    {Energy Missile\label{pwr:energy_missile}}
    {2nd-level Psychokinesis}
    {1 action}
    {120 feet}
    {MB 2, PD 3}
    {Instantaneous}
    {Sight, Line of Effect}
Upon manifesting this power, you choose cold,
lightning, fire, or thunder. You release a powerful missile
of energy of the chosen type at up to five creatures you can
see in range and have line of effect to. Make a psionics attack
against each target. On a hit, the missile deals 3d6 points
of damage of the chosen type. You cannot hit the same target
multiple times with the same manifestation of this power.

\subparagraph{Cold} A missile of this energy type deals +1
point of damage per die. The saving throw to reduce damage
from a cold missile is a Constitution save instead of a Dexterity
save.

\subparagraph{Lightning} Manifesting a missile of this energy
type provides a +2 bonus to the attack roll against creatures
wearing metal armour.

\subparagraph{Fire} A missile of this energy type deals +1
point of damage per die.

\subparagraph{Thunder} A missile of this energy type deals
-1 point of damage per die but reduces an opponent's AC by
1 for this attack only.
\augment{For every additional psi die you spend, this power's
damage increases by 1d6.
}
\DndPowerHeader%
    {Energy Push\label{pwr:energy_push}}
    {2nd-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 2, PD 3}
    {Instantaneous}
    {Sight, Line of Effect}
Upon manifesting this power, you choose cold,
lightning, fire, or thunder. You project a solid blast of
energy of the chosen type at a target in range that you
can see and have line of effect to. The target must make
a Dexterity saving throw, suffering from 4d6 points of damage
of the chosen type if they fail.

In addition, if the target is
up to one size category larger than you and fails a Strength
saving throw, the driving force of the energy blast pushes
it back 5 feet plus another 5 feet for every 5 points of
damage it takes.

If a wall or other solid object prevents
the subject from being pushed back, the subject instead
slams into the object and takes an extra 2d6 points of damage
from the impact (no save).

\subparagraph{Cold}
A blast of this energy type
deals +1 point of damage per die.
This does not apply to the slam damage.
The saving throw to reduce damage from a cold push
is a Constitution save instead of a Dexterity save.

\subparagraph{Lightning}
Manifesting a blast of this energy type provides a +2 bonus
to the save DC if the target is wearing metal armour.

\subparagraph{Fire}
A blast of this energy type deals +1
point of damage per die (damage from impact remains at
2d6 points).

\subparagraph{Thunder}
A blast of this energy
type deals -1 point of damage per die
(damage from impact
remains at 2d6 points)
but provides a +1 bonus to the save DC.
\augment{For every 2 additional psi dice you spend, this power's
damage increases by one die (d6) and its save DC increases
by 1. The damage increase applies to both the initial blast
and any damage from a creature impacting with an object.
}
\DndPowerHeader%
    {Energy Ray\label{pwr:energy_ray}}
    {1st-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 1, PD 1}
    {Instantaneous}
    {Sight, Line of Effect}
Upon manifesting this power,
you choose cold, lightning, fire, or thunder.
You create a ray of energy of the chosen type that
shoots forth from your fingertip and strikes a target within range
that you can see and have line of effect to,
dealing 2d6 points of damage if you succeed on a
ranged psionics attack with the ray.
The type of damage depends on
the type of energy of the ray you manifest. 
\subparagraph{Cold}
  A ray of this energy deals +1 point of cold damage per die.
\subparagraph{Lightning}
  Manifesting a ray of this energy type provides a
  +2 bonus on your attack roll if the target is wearing metal armour.
\subparagraph{Fire}
  A ray of this energy type deals +1 point of fire damage per die.
\subparagraph{Thunder}
  A ray of this energy type deals -1 point of thunder damage per die
  but reduces an opponent's AC by 1.
\augment{For every additional psi die you spend, this power's
damage increases by 1d6.
}
\DndPowerHeader%
    {Energy Transformation\label{pwr:energy_transformation}}
    {7th-level Prana Bindu}
    {1 action}
    {Self (30-foot line), see text}
    {MB 5, PD 13}
    {Concentration, up to 10 minutes}
    {None}
Your bodily assimilates some of the effects
of an energy attack and converts it into a jet of plasma.
When you manifest this power, the total amount of cold, fire,
lightning or thunder damage that you take from separate sources
is reduced by 10, to a minimum of 0. The amount of damage
that has been reduced is `absorbed'. You also have advantage
on saving throws to maintain concentration on powers if the
saving throw was prompted by damage of the aforementioned
types. \emph{Note:} if a separate source of damage is absorbed
and reduced to zero damage,
you do not need to make a Constitution saving throw
to maintain concentration on any powers.

Whenever you absorb damage, you store up the energy and can
later discharge it as a jet of plasma. To discharge a ray
requires a standard action. The ray emerges from you as a
30-foot line with a width of 5 feet. Each creature caught
in the path of the ray takes damage equal to the amount of
energy damage you have stored on a failed save, or half as
much on a successful save. However, the total damage is capped
at five times your psionic threshold. The ray you fire
does fire or lightning damage (you may decide on the type).

You can choose to fire any number of rays during the power's
duration. As long as this power remains in effect, you can
continue to absorb energy damage and fire additional rays
using the stored damage.

\DndPowerHeader%
    {Energy Wave\label{pwr:energy_wave}}
    {7th-level Psychokinesis}
    {1 action}
    {Self (60-foot cone)}
    {MB 6, PD 13}
    {Instantaneous}
    {None}
Upon manifesting this power,
you choose cold, lightning, fire, or thunder.
You create a flood of energy of the chosen type
that deals 13d6 points of damage
to each creature and object in a 60-foot cone
centred on yourself that fails a Dexterity saving throw,
or half as much on a successful save.
This power originates at your hand
and extends outward in a 60-foot cone.

\subparagraph{Cold}
A wave of this energy type deals +1 point
of damage per die.
The saving throw to reduce damage from a cold wave
is a Constitution save instead of a Dexterity save.  

\subparagraph{Lightning}
Manifesting a wave of this energy type
provides a +2 bonus to the save DC if the target is wearing
metal armour.

\subparagraph{Fire}
A wave of this energy type deals +1 point of damage per die.

\subparagraph{Thunder}
A wave of this energy type deals -1 point of damage per die
but grants a +1 bonus to the save DC.
\augment{For every additional psi die you spend, this power's
damage increases by 1d6. For each extra two dice of damage, this
power's save DC increases by 1.
}
\DndPowerHeader%
    {Envenom\label{pwr:envenom}}
    {1st-level Prana Bindu}
    {1 bonus action}
    {Touch}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {None}
Your saliva briefly turns into a caustic
bile which does no damage to you, but can damage your enemies.
You may use your bonus action to coat one weapon you are holding
with the bile. The next time you hit with that weapon, the
bile deals 2d4 acid damage.

After the hit, roll 1d10. On a roll of 10, the bile totally
corrodes the weapon you coated, and it is destroyed (unless
it is a magic weapon, resistant to acid damage or otherwise
impervious to physical damage).

\DndPowerHeader%
    {Fist of Fury\label{pwr:fist_of_fury}}
    {3rd-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 3, PD 5}
    {Concentration, up to 10 minutes}
    {None}
Your fists become fuelled with terrifying
power. While the power lasts, any unarmed attack you make
with your fist scores a critical hit on a roll of 18, 19 or
20.

\DndPowerHeader%
    {Flame Choke\label{pwr:flame_choke}}
    {1st-level Prana Bindu}
    {1 grapple}
    {Self}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
Your vice-like grip burns those that oppose
you. Whenever you attempt to grapple a creature, you may freely
manifest this power. If the grapple attempt
is successful, the target immediately takes 2d6 fire damage.
On every turn you start while the target is still grappled,
the target takes an additional 2d6 fire damage. Whenever the
grapple ends, the target must succeed on a Strength saving
throw or fall prone.

\DndPowerHeader%
    {Float\label{pwr:float}}
    {1st-level Spacefolding}
    {1 action}
    {Self}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {None}
You mentally support yourself in water or
similar liquid. You gain a swim speed equal to your base movement
speed for the power's duration, or use the power to boost
your swim speed by 10 feet if you already have one.

\DndPowerHeader%
    {Force Screen\label{pwr:force_screen}}
    {1st-level Psychokinesis}
    {1 bonus action}
    {Self}
    {MB 2, PD 1}
    {Concentration, up to 1 minute}
    {None}
You create an invisible mobile disk of force
that hovers in front of you. The force screen provides a +2
bonus to your AC until the power ends.
\augment{For every 4 additional psi dice you spend, the bonus
to your AC from the force screen improves by 1.
}
\DndPowerHeader%
    {Fusion\label{pwr:fusion}}
    {8th-level Prana Bindu}
    {1 action}
    {Touch}
    {MB 8, PD 15}
    {Concentration, up to 1 minute}
    {None}
You and another willing, corporeal, living
creature of the same or smaller size fuse into one being.
As the manifester, you control the actions of the fused being.
However, you can give up this control to the other creature.
Once you give up control, you cannot regain it unless the
other creature relinquishes it.

The fused being has your current hit points plus the other
creature's current hit points. The fused being knows all
the powers you and the other creature know, has the sum of
your and the other creature's psi dice, has the sum of your
and the other creature's spell slots, and knows or has prepared
any spells you or the other creature possesses (if any). Likewise,
all feats, racial abilities, and class features are pooled
(if both creatures have the same ability, the fused being
gains it only once). For each of the six ability scores, the
fused being's score is the higher of yours and the other
creature's, and the fused being also has the higher hit dice
and psionic threshold; this effectively means the fused being
uses the better saving throws, attack bonus, and skill modifiers
of either member, and it manifests powers up to the higher
of the psionic thresholds that you or the other creature possessed
before becoming fused.

You decide what equipment is absorbed into the fused being
and what equipment remains available for use. These fused
items are restored once the power ends.

When the power ends, the fused being separates. The other
creature appears in an area adjacent to you that you determine.
If separation occurs in a cramped space, the other creature
is expelled through the Astral Plane, finally coming to rest
materially in the nearest empty space and taking 1d6 force
damage for each 10 feet of solid material passed through.

Damage taken by the fused being is split evenly between you
and the other creature when the power ends. You do not leave
the fusion with more hit points than you entered it with,
unless you were damaged prior to the fusion and the fused
being was subsequently healed. In a like manner, the fused
being's remaining psi dice are split between you and
the other creature (you can leave with more psi dice than you
entered with, as long as you don't exceed the maximum psi dice
for your level and ability score).

If a fused being is killed, it separates into its constituent
creatures, both of which are also dead.

\DndPowerHeader%
    {Grip of Iron\label{pwr:grip_of_iron}}
    {1st-level Prana Bindu}
    {1 bonus action or reaction, see text}
    {Self}
    {MB 1, PD 1}
    {Until the end of your current turn}
    {None}
You can improve your chances in a grapple
as a bonus action, gaining a +3 bonus on a grapple checks
until the end of your current turn.

In addition, you can also manifest this power as a reaction
to being grappled; in this case, you shrug off your opponent's
grip with great strength. You gain a +3 bonus to the check
to avoid being grappled, but your must make a
Strength (Athletics) check
i.e. you cannot choose a Dexterity (Acrobatics) check instead.
\augment{For every 3 additional psi dice you spend, the bonus
increases by 1.
}
\DndPowerHeader%
    {Hammer\label{pwr:hammer}}
    {1st-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 1, PD 1}
    {1 round}
    {None}
This power charges your touch with the force
of a sledgehammer. Until the end of your next turn, if you
make a successful unarmed attack against any creature or object,
you use 1d12 for your damage dice.
\augment{For every additional psi die you spend, the power's
duration increases by 1 round.
}
\DndPowerHeader%
    {Hyperphantasm\label{pwr:hyperphantasm}}
    {2nd-level Voice}
    {1 action}
    {60 feet}
    {MB 2, PD 5}
    {Concentration, up to 1 minute}
    {Sight}
Your inner Voice convinces the mind of another that an illusory image
is in fact real. Choose a creature you can see in range.
The target must make an Intelligence saving throw.
On a failed save, the mind of the target becomes aware of a phantasmic
object or phenomenon---for example a change in temperature, pressure
or the appearance of an object---only perceivable by them.
You then stipulate the exact nature of the phantasm,
which cannot be changed from this while you maintain concentration
on the power. Moreover, the phantasm cannot be larger than a 10-foot cube
or appear to affect a volume greater than the extent of the cube,
whichever applies, and cannot be discontinuous.
The phantasm can be moved freely either on your turn (requiring no action)
or as stipulated by the initial conditions of the phantasm
(for example if you specified the phantasm to be a wicker basket
over the target's head which moves with them).
The phantasm has no grounding in the physical world,
only existing in the target's mind because of their fooled senses.

A target affected by this power acts as if the phantasm were real
unless their passive Intelligence (Investigation) is higher
than your psionics save DC,
in which case the illusion persists until the power ends
but appears patently false
(and therefore they do not suffer the effects described below).
A target acting as if the phantasm is real rationalises any illogical
outcomes which arise from interacting with the phantasm,
even if the outcome is absurd or plainly at odds with the natural order.
For example, a target attempting to walk across a phantasmal bridge
that spans a chasm falls once it steps onto the bridge.
If the target survives the fall, it still believes that the bridge exists
and comes up with some other explanation for its fall---it was pushed,
it slipped, or a strong wind might have knocked it off.

An affected target is so convinced of the phantasm's reality
that it can even take damage from the illusion.
A phantasm created to appear as a creature can attack the target.
Similarly, a phantasm created to appear as fire, a pool of acid,
or lava can burn the target. Each round on your turn,
the phantasm can deal 1d6 psychic damage to the target
if it is in the phantasm's area or within 5 feet of the phantasm,
provided that the illusion is of a creature or hazard
that could logically deal damage, such as by attacking.
The target perceives the damage as a type appropriate to the illusion.

However, if as a result of stimuli extrinsic to the phantasm itself,
the target has reason to believe that the phantasm is illusory, 
they may make an Intelligence (Investigation) check to examine the phantasm
against your psionics save DC.
If the check succeeds, the target realises that the phantasm is not real,
and the power ends.
For example, an ally to the target may notice the target's erratic or
illogical behaviour, and suggest to them that they are being afflicted
by an illusion. This counts as sufficient reason to doubt the phantasm.
\augment{For every 4 additional psi dice you spend,
this power can affect one additional creature.
The additional creature must be within 15 feet of another creature
affected by the same manifestation of this power.
}
\DndPowerHeader%
    {Identify Psionics\label{pwr:identify_psionics}}
    {1st-level Prescience}
    {1 minute}
    {Touch}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
As the \spell{identify} spell, except for
items imbued with psionics and creatures manifesting powers.

\DndPowerHeader%
    {Immovability\label{pwr:immovability}}
    {4th-level Prana Bindu}
    {1 action}
    {Self}
    {MB 4, PD 7}
    {Concentration, up to 1 hour}
    {None}
You are almost impossible to move.
Your weight does not vary;
instead, your body adjusts itself to withstand immense amounts
of force. You could conceivably do this in mid-air. You have
a +10 bonus on any check or saving throw against being moved.
You can't voluntarily move to a new location unless you stop
concentrating, which ends the power.

While under the effects of this power, you cannot add your
Dexterity bonus to your AC; however, your anchored body gains
damage threshold (10).

You cannot make physical attacks or perform any other large-scale
movements (you can make small-scale movements, such as breathing,
turning your head, moving your eyes, talking, and so on).
\augment{If you spend 6 psi dice, you can manifest
this power as a reaction to being involuntarily moved.
}
\DndPowerHeader%
    {Inertial Armour\label{pwr:inertial_armour}}
    {1st-level Psychokinesis}
    {1 action}
    {Touch}
    {MB 1, PD 1}
    {8 hours}
    {None}
Your mind forms a dampening barrier against physical attacks.
You touch a willing creature who isn't wearing armour.
Until the power ends, the target's base AC becomes 13
plus its Intelligence modifier.
The power ends early if the target dons armour.

\DndPowerHeader%
    {Inertial Dampener\label{pwr:inertial_dampener}}
    {4th-level Psychokinesis}
    {1 action}
    {Self}
    {MB 4, PD 7}
    {Concentration, up to 10 minutes}
    {None}
You create a skin-tight psychokinetic barrier
around yourself that resists blunt-force blows and explosions.
You become immune to all bludgeoning damage for the power's duration,
including that caused by psionic or magic items.

\DndPowerHeader%
    {Inflict Pain\label{pwr:inflict_pain}}
    {2nd-level Voice}
    {1 action}
    {30 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {Speech, Sight}
You Voice stabs at the mind of your foe,
unleashing torrents of horrible agony. Choose a creature in
range that you can see and that can hear and understand you.
They must succeed on a Wisdom saving
throw or suffer wracking pain that imposes disadvantage on
their attack rolls and skill checks.
\augment{For every 2 additional psi dice you spend, this power's
save DC increases by 1, and the power can affect an additional
target. Any additional target cannot be more than 15 feet from
another target of the power.
}
\DndPowerHeader%
    {Ironflesh\label{pwr:ironflesh}}
    {5th-level Prana Bindu}
    {1 action}
    {Self}
    {MB 5, PD 9}
    {Concentration, up to 1 minute}
    {None}
Your skin turns as solid as iron, rendering it profoundly
more resistant to physical assaults.
Reduce your Dexterity score by 4 but increase your Strength by 2,
up to a maximum of 22.
You gain damage resistance (10) and a +5 bonus to your AC.
You also gain immunity to the deafened, poisoned and stunned conditions,
immunity to poison damage,
and you become resistant to all damage.

\DndPowerHeader%
    {Leap\label{pwr:leap}}
    {2nd-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 2, PD 3}
    {Until the end of your current turn}
    {None}
Your body prepares itself to undertake an
incredible feat of agility and strength. As a bonus action,
you can propel yourself across vast distances. You gain a
flying speed equal to your base movement speed until the end
your current turn. For example, if you have taken the dash
action on your turn to double your base movement speed, the
fly speed you gain would be equal to that doubled speed.
\augment{If you spend 3 additional psi dice, any movement with
this fly speed does not provoke opportunity attacks.
}
\DndPowerHeader%
    {Levitate\label{pwr:levitate}}
    {2nd-level Spacefolding}
    {1 action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 10 minutes}
    {None}
As the \spell{levitate} spell, except when
manifested the target can only be the manifester themselves,
not any other creature or a loose object.

\DndPowerHeader%
    {Manipulate Creature With Mind\label{pwr:manipulate_creature_with_mind}}
    {4th-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 3, PD 7}
    {Concentration, up to 1 minute}
    {Sight}
You deal psychokinetic blows at a distance
against creatures you can see. For the power's duration,
you can perform the shove, disarm or grapple action without
needing to be in melee range (however, the target needs to
be within the power's range).
Resolve these attempts as normal. Wherever you
would make a Strength (Athletics) check or attack roll, use
your psionics attack modifier for the roll.
\augment{For every additional psi die you spend, this power
grants a +1 bonus on all rolls you make with his power to shove,
grapple and disarm.
}
\DndPowerHeader%
    {Manipulate Object With Mind\label{pwr:manipulate_object_with_mind}}
    {3rd-level Psychokinesis}
    {1 action}
    {120 feet}
    {MB 2, PD 5}
    {Concentration, up to 1 minute}
    {Sight}
By focusing your mind, you are able to manipulate
objects as you desire. Choose an object you can see within
range weighing no more than 250 pounds. Each turn you spend
concentrating on this power, including the turn in which you
manifest this power, you may move the object up to 20 feet.
This power ends if the object is moved out of range or you
can no longer see the object, and if you cease concentration,
the object falls or stops.

You may drop the object and pick up another during the same
turn as long as you don't stop concentrating on the power.
You may also exert fine control on the objects you move. The
object does not move fast enough to cause any damage when
being rammed into other creatures or objects, however it can
cause damage to creatures and objects if it is dropped onto
them. In this case,
the object or creature deals as much bludgeoning
damage as it would take from the fall itself. If the object
falls onto a creature, they must make a Dexterity saving throw,
taking the full damage on a failed save and no damage on a
successful save.

If the object you are attempting to move is being carried,
worn or is equipped to a creature in some way, the creature
can prevent you from moving the object. If they do so, make
an ability check with your psionics ability modifier (not
psionics attack modifier) contested by their Strength check.
If they win the contest, you cannot move that and any other
object until your turn ends. If the contest ends in a draw,
you cannot move that object, but you may attempt to move others.
\augment{For every additional psi die you spend, the weight
limit of the target increases by 25 pounds.
}
\DndPowerHeader%
    {Matter Agitation\label{pwr:matter_agitation}}
    {1st-level Psychokinesis}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {Sight}
You can excite the structure of a non-psionic,
non-magical object that you can see,
heating it to the point of combustion over time.
The agitation grows more intense in the second and third rounds
after you manifest the power, as described below.

\subparagraph{1st Round}
  Readily flammable material
  (paper, dry grass, tinder, torches) ignites.
\subparagraph{2nd Round}
  Wood smoulders and smokes,
  metal becomes hot to the touch,
  paint shrivels, water boils.
\subparagraph{3rd and Subsequent Rounds}
  Wood ignites, metal scorches
  (1d4 points of damage for those holding metallic objects),
  lead melts.

\DndPowerHeader%
    {Mind Blank, Psionic\label{pwr:mind_blank_psionic}}
    {6th-level Voice}
    {1 action}
    {Touch}
    {MB 6, PD 11}
    {24 hours}
    {None}
As the \spell{mind blank} spell, except as
noted here. You conceal your mind---or the mind of one creature
you touch---from outside influence, rendering it effectively
invisible.

\DndPowerHeader%
    {Mind Palace, Power\label{pwr:mind_palace_power}}
    {4th-level Psychokinesis}
    {1 reaction, see text}
    {Self}
    {MB 4, PD 7}
    {1 round, see text}
    {None}
As a reaction to when you or an ally within
20 feet of you is targeted by an attack or subject to a harmful
psionic effect, you encase yourself and your allies in a shimmering
palace of psychokinetic force. The palace is a sphere of radius
20 feet centred on you. All damage from powers and innate
talents taken by subjects inside the area of the mind palace
is halved. This lowering takes place prior to the effects
of other powers or abilities that lessen damage. The palace
lasts until the start of your next turn. $^*$Not to be confused
with the \emph{mind palace} ability.
\augment{For every additional psi die you spend, this power's
duration increases by 1 round.
}
\DndPowerHeader%
    {Mind Thrust\label{pwr:mind_thrust}}
    {1st-level Voice}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
You instantly deliver a massive assault on
the thought pathways of any one creature in range. The target
must succeed on an Intelligence saving throw or take 1d12
points of psychic damage.
\augment{For every additional psi dice you spend, the power's
damage increases by 1d12.
}
\DndPowerHeader%
    {Missive\label{pwr:missive}}
    {1st-level Voice}
    {1 action}
    {60 feet}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
You send a telepathic message of up to ten
words to any living creature within range. Missive is strictly
a one-way exchange from you to the target. If you do not share
a common language, the target `hears' meaningless mental
syllables.
\augment{For every 2 additional psi dice you spend, the power's
range increases by 5 feet.
}
\DndPowerHeader%
    {Object Reading\label{pwr:object_reading}}
    {2nd-level Prescience}
    {1 minute}
    {Touch}
    {MB 2, PD 3}
    {Concentration, up to 10 minutes}
    {None}
You can learn details of an inanimate object's
previous owner.
Objects accumulate psychic impressions
left by their previous owners,
which can be read by use of this power.
The amount of information revealed depends
on how long you study a particular object.

\subparagraph{1st Minute}
  Last owner's race.
\subparagraph{2nd Minute}
  Last owner's gender.
\subparagraph{3rd Minute}
  Last owner's age.
\subparagraph{4th Minute}
  Last owner's alignment.
\subparagraph{5th Minute}
  How last owner gained and lost the object.
\subparagraph{6th+ Minute}
  Next-to-last owner's race, and so on.

The power always correctly identifies the last owner of the item,
and the original owner
(if you keep the power active long enough).
There is a 90\% chance
that this power will successfully identify all other former owners
in sequence,
but there is a 10\% chance that one former owner
will be skipped and thus not identified.

This power will not identify casual users as owners
(anyone who uses an object to attack someone
or something is not thereafter considered a casual user).
An object without any previous owners reveals no information.

You can continue to run through a list of previous owners
and learn details about them as long as the power's duration lasts.
If you use this power additional times on the same object,
the information yielded is the same
as if you were using the power on the object for the first time.
\augment{For every additional psi die you spend, this power's
maximum duration increases by 10 minutes.
}
\DndPowerHeader%
    {Orient Self\label{pwr:orient_self}}
    {1st-level Prescience}
    {1 action}
    {Self}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
You generally know where you are. This power
is useful to characters who end up at unfamiliar destinations
after teleporting, using a gate, or travelling to or from
other planes of existence. The power reveals general information
about your location as a feeling or presentiment. The information
is usually no more detailed than a summary that locates you
according to a prominent local or regional site. Using this
power also tells you what direction you are facing.

\DndPowerHeader%
    {Plane Shift, Psionic\label{pwr:plane_shift_psionic}}
    {5th-level Spacefolding}
    {1 action}
    {Touch}
    {MB 4, PD 9}
    {Instantaneous}
    {None}
Your mind warps space and time, allowing
you to move yourself or some other willing creature to another plane
of existence or alternate dimension. If several willing persons
link hands in a circle, as many as eight can be affected by
the plane shift at the same time. Unlike the \spell{plane
shift} spell, precise accuracy as to a particular arrival
location on the intended plane is nigh impossible, unless
you are attuned to a planar beacon or have some other means
of anchoring yourself in one plane. Without these items, when
you travel to another plane of existence, you appear 5 to
500 miles (5d100) from your intended destination.
\augment{For every 3 additional psi dice you spend, roll one
less d100 when determining how close you arrive to your intended
destination.
}
\DndPowerHeader%
    {Possible Futures\label{pwr:possible_futures}}
    {4th-level Prescience}
    {1 action}
    {Self}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {None}
You take a hand in influencing the probable
outcomes of your immediate environment. You see the many alternative
branches that reality could take in the next few seconds,
and with this foreknowledge you gain the ability to, while
this power lasts, reroll one attack roll, one saving throw,
one ability check, or one skill check each round. You must
take the result of the reroll, even if it's worse than the
original roll. You do not have to make another roll if satisfied
with your original roll. The roll must be made by yourself.

\DndPowerHeader%
    {Power Pirate\label{pwr:power_pirate}}
    {6th-level Voice}
    {1 action}
    {60 feet}
    {MB 5, PD 11}
    {Concentration, up to 1 round per psionic threshold}
    {Sight}
You use your Voice to take over control of a power
requiring concentration that was manifested
by a creature you can see in range.
The target of this power is the manifesting creature.

Once you wrest control of the power from the target,
you have several options.
\begin{itemize}
  \item Allow the power to function as normal.
  \item Keep the power targeted on the manifesting creature
        (if a power with a target of self) but decide how
        the power fulfils its function each round.
  \item Retarget the power on yourself
        (if a power with a target of self).
  \item Choose not to concentrate on the usurped power
          in the next round, ending the power at that point.
\end{itemize}
When the duration of \power{power pirate} expires,
the power you took control of ends
(even if this would mean that the power ends earlier than normal).

\DndPowerHeader%
    {Precognition\label{pwr:precognition}}
    {1st-level Prescience}
    {1 bonus action}
    {Self}
    {MB 2, PD 1}
    {Concentration, up to 1 minute}
    {None}
Your awareness of your immediate circumstances extends
a fraction of a second into the future,
granting you an edge over your opponents and environment.
Choose a variation from the list below.
The nature of the benefit conferred to you
depends on the chosen variant.

\subparagraph{Defensive}
  You gain a +2 bonus to your AC and all saving throws.

\subparagraph{Anticipatory}
  You gain a +2 bonus to attack rolls.

\subparagraph{Offensive}
  You gain a +3 to bonus to your damage rolls.
\augment{For every 3 additional psi dice you spend, the bonus you
have gained from a variant increases by 1 to a maximum of 4.
}
\DndPowerHeader%
    {Psi Door\label{pwr:psi_door}}
    {4th-level Spacefolding}
    {1 action}
    {500 feet}
    {MB 3, PD 7}
    {Instantaneous}
    {None}
As the \spell{dimension door}, except as
noted here.
\augment{If you spend 6 additional psi dice, you can manifest
this power as a bonus action.
}
\DndPowerHeader%
    {Psi Hand\label{pwr:psi_hand}}
    {1st-level Psychokinesis}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {None}
As the \spell{mage hand} spell.

\DndPowerHeader%
    {Psi Vision\label{pwr:psi_vision}}
    {2nd-level Prescience}
    {1 action}
    {Self}
    {MB 2, PD 3}
    {8 hours}
    {None}
As the \spell{darkvision} spell.

\DndPowerHeader%
    {Psi Wall\label{pwr:psi_wall}}
    {4th-level Metacreativity}
    {1 action}
    {30 feet}
    {MB 4, PD 7}
    {Concentration, up to 1 minute}
    {Sight, Mundane matter}
You fashion a great wall of raw material
which erupts from the earth at a point you can see within
range. The wall cannot move once it is formed. The origin
of the wall must be within range, but it can extend past this
power's range. It is 1 inch thick per psionic threshold and
has a side length of 10 feet per psionic threshold. You can
also choose to form the wall into a sphere or hemisphere with
a radius of up to 1 foot per psionic threshold. The wall must
be continuous and unbroken when manifested. If its surface
is interrupted by any object or creature, the power fails.

Each 10-foot panel of the wall (or section of surface area
100 ft.$^2$) has 10 hit points per inch of thickness and damage
immunity (5). A section of the wall whose hit points drop
to 0 is breached and can be passed through. Otherwise, if
a creature tries to break through the wall, they can do so
with a successful Strength check with DC equal to 15 + the
number of inches it is thick.

The wall is susceptible to the \power{dispel psionics} power,
but it gains a +4 bonus on any check to determine whether
the wall is negated in such a way. Spells and breath weapons
cannot pass through the wall in either direction, since the
wall provides total cover (though they could damage it). Powers
which ordinarily do not require line of effect cannot target
creatures or objects on the opposite side of the wall. However,
the wall does not block travel by Spacefolding. The wall is
opaque, and thus a creature on one side does not have sight
of creatures or objects on the other side.

\DndPowerHeader%
    {Psionic Golem\label{pwr:psionic_golem}}
    {1st-level Metacreativity}
    {1 action}
    {30 feet}
    {MB 1, PD 1}
    {Up to 1 hour}
    {Mundane matter}
\textit{Note: you cannot manifest this power
unless you have learnt the \secref{subs:menu_a} Metacreativity tenet.}

You weave mundane matter into an autonomous construct---vaguely
resembling a humanoid creature of your choosing---that acts as you command.
This power creates one 1st-level psionic golem
(see \secref{sec:psionic_golem})
that attacks your enemies. It appears where you designate
in range and acts whenever you end your turn (it still technically
acts on your turn, however). It attacks your opponents to
the best of its ability. As a free action, on your turn you can mentally
direct it not to attack, to attack particular enemies, or
to perform other actions. The psionic golem acts normally
on the last round of the power's duration and dissipates
after you finish your turn. Otherwise, it dissipates when
it is reduced to 0 hit points, ending the power.
\augment{For every 3 additional psi dice you spend, the level
of the psionic golem increases by 1.
}
\DndPowerHeader%
    {Psionic Golem, Repair\label{pwr:psionic_golem_repair}}
    {2nd-level Metacreativity}
    {1 action}
    {Touch}
    {MB 2, PD 3}
    {Instantaneous}
    {Mundane matter}
When laying your hands upon a psionic golem
that has at least 1 hit point remaining, you reknit its structure
to repair damage it has taken. The power repairs 3d8 + your psionic
threshold points of damage. Constructs that
are immune to psionics or magic cannot be repaired in this
fashion.
\augment{For every 2 additional psi dice you spend, this power
repairs an additional 1d8 hit points.
}
\DndPowerHeader%
    {Psionic Step\label{pwr:psionic_step}}
    {2nd-level Spacefolding}
    {1 bonus action}
    {Self}
    {MB 2, PD 3}
    {Instantaneous}
    {None}
You create a brief, unstable link between
two nearby locations, allowing you to jump from one spot to
another. You teleport to an unoccupied space you can see up
to 30 feet from you.
\augment{For every 2 additional psi dice you spend, you can
teleport an extra 10 feet.
}
\DndPowerHeader%
    {Psychic Archaeology\label{pwr:psychic_archaeology}}
    {2nd-level Prescience}
    {1 hour}
    {60 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 hour}
    {None}
You gain historical vision in a given location.
Rooms, streets, tunnels, and other discrete locations accumulate
psychic impressions left by powerful emotions experienced
in a given area. These impressions offer you a picture of
the location's past.

The types of events most likely to leave psychic impressions
are those that elicited strong emotions: battles and betrayals,
marriages and murders, births and great pain, or any other
event where one emotion dominates. Everyday occurrences leave
no residue for a manifester to detect.

The vision of the event is dreamlike and shadowy. You do not
gain special knowledge of those involved in the vision, though
you might be able to read large banners or other writing if
they are in your language.

Beginning with the most recent significant event at a location
and working backward in time, you can sense one distinct event
for every 10 minutes you maintain concentration, if any such
events exist to be sensed. Your sensitivity extends into the
past a maximum number of years equal to 200 times your psionic
threshold.

\DndPowerHeader%
    {Psychic Beacon\label{pwr:psychic_beacon}}
    {2nd-level Prescience}
    {1 action}
    {30 feet}
    {MB 2, PD 3}
    {24 hours}
    {Sight}
By manifesting this power, you place a psionic signature on a creature
or an unattended object that you can see in range.
If you target a creature, the signature is placed on that creature
if they fail a Wisdom saving throw.
You can automatically detect the presence of the signature
whenever it is within 1,000 feet of you,
and in such cases you know the direction and approximate distance
to the target object or creature.

If the distance between you and the psychic beacon
increases beyond 1,000 feet, you can determine the direction
and approximate distance to the signature object or creature
by using an action.
\augment{You can augment this power in one or both of the following ways.
\begin{itemize}
  \item For every 2 additional psi dice you spend,
    this power's save DC (if applicable) increases by 1.
  \item If you spend 4 additional power points,
    you can designate a willing creature to detect the beacon.
    You must touch the creature as you manifest the power.
    For the duration of the power,
    that creature senses the location of the beacon instead of you.
  \end{itemize}
}
\DndPowerHeader%
    {Psychic Crush\label{pwr:psychic_crush}}
    {5th-level Voice}
    {1 action}
    {60 feet}
    {MB 4, PD 9}
    {Instantaneous}
    {Sight}
You abruptly and brutally crush
the mental essence of any one creature you can see, debilitating
its acumen. The target must succeed on a Wisdom saving throw
or take 7d12 psychic damage. If they succeed, they instead
take 4d6 psychic damage.
\augment{For every 2 additional psi dice you spend, the damage
on a successful save increases by 1d6.
}
\DndPowerHeader%
    {Psychofeedback\label{pwr:psychofeedback}}
    {5th-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 5, PD 9}
    {1 minute}
    {None}
You can readjust your body to boost one physical
ability score at the expense of one or more of the other scores.
Select one ability score you would like to boost, and increase
it by the same amount that you decrease one or more other
scores.

You can boost your Strength, Dexterity or Constitution score
by an amount equal to your psionic threshold (or any lesser
amount), assuming you can afford to burn your other ability
scores to such an extent. You may boost your ability scores
past 20 in this fashion.

When the duration of this power expires, your ability boost
ends, but your ability score decrease remains until you
finish a long rest.

\DndPowerHeader%
    {Rapid Healing\label{pwr:rapid_healing}}
    {3rd-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 2, PD 5}
    {Instantaneous}
    {None}
You mind takes control of your body's healing
process, rapidly speeding it up. You gain hit points equal
to 1d12 + your psionics ability modifier.
\augment{For every 2 additional psi dice you spend, this power heals
an additional 1d8 points of damage.
}
\DndPowerHeader%
    {Recall\label{pwr:recall}}
    {1st-level Prescience}
    {1 minute}
    {Self}
    {MB 1, PD 1}
    {Instantaneous}
    {None}
By meditating on a subject, you can recall
natural memories and knowledge otherwise inaccessible to you.

When you fail a History, Religion, Arcana or Nature check,
you can manifest this power to, at the end of the power's
manifesting time, repeat the check. If successful, you instantly
recall what was previously buried in your subconscious.

\DndPowerHeader%
    {Remote Viewing Trap\label{pwr:remote_viewing_trap}}
    {6th-level Prescience}
    {1 action}
    {Self}
    {MB 5, PD 11}
    {24 hours}
    {None}
When others use any means of scrying you
from afar, your prepared trap gives them a nasty surprise.
If the scryer fails a Wisdom saving throw when it attempts
to scry you, you are undetected. Moreover, the would-be observer
takes 8d6 lightning damage. If the scryer succeeds its saving
throw, it takes only half as much damage and is able to observe
you normally.

Either way, you are aware of the attempt to view you, but
not of the viewer or the viewer's location.

\DndPowerHeader%
    {Restore Extremity\label{pwr:restore_extremity}}
    {5th-level Prana Bindu}
    {1 action}
    {Touch}
    {MB 5, PD 9}
    {Instantaneous}
    {None}
You restore a severed extremity to a creature
that has lost a digit, hand, arm, leg, or even its head. This
power does not restore life, but it returns a lost extremity
to a living or dead creature if the creature is otherwise
mostly intact. The original extremity need not be present
when this power is manifested; a new extremity is created
by the power. If a head is restored to a body, the original
head (if not already destroyed) loses all spark of identity,
and can be considered as dead tissue.

\DndPowerHeader%
    {Resuscitation\label{pwr:resuscitation}}
    {3rd-level Voice}
    {1 action}
    {30 feet}
    {MB 3, PD 5}
    {Instantaneous}
    {Speech$^*$, Sight}
Your Voice commands a creature back to life.
If a creature you can see within range has died in between
your previous turn and your current turn, you may as an action
return them to life with 1 hit point. This power can't return
to life a creature that has died of old age, nor can it restore
any missing body parts.
$^*$A creature need not hear or understand you to be affected
by your Voice.

\DndPowerHeader%
    {Retrieve\label{pwr:retrieve}}
    {6th-level Spacefolding}
    {1 action}
    {60 feet}
    {MB 5, PD 11}
    {Instantaneous}
    {Sight}
You automatically teleport an item you can
see within range directly to your hand. The item can weigh
up to 10 times your psionic threshold in pounds. If the object
is in the possession of an opponent, it comes to your hand
if your opponent fails a Dexterity saving throw.
\augment{For every additional two psi dice you spend, the weight
limit of the target increases by 10 pounds.
}
\DndPowerHeader%
    {Reveal Agony\label{pwr:reveal_agony}}
    {2nd-level Prescience}
    {1 action}
    {60 feet}
    {MB 2, PD 3}
    {Instantaneous}
    {Sight}
The fabric of time parts to your will, revealing
wounds a creature in range that you can see
is yet to receive. If the target
fails a Wisdom saving throw, the target takes 4d6 psychic
damage as the future impinges briefly on the present.
\augment{For every additional psi die you spend, this power's
damage increases by 1d6 points. For each extra 2d6 points
of damage, this power's save DC increases by 1.
}
\DndPowerHeader%
    {Sacrificial Shell\label{pwr:sacrificial_shell}}
    {3rd-level Metacreativity}
    {1 reaction, which you take when making a saving throw against certain damage types, see text}
    {Self}
    {MB 3, PD 5}
    {Instantaneous}
    {Mundane matter}
You instantly weave a protective shell around
you which absorbs damage and then falls of. When you make
a saving throw against an effect which would deal fire, cold,
lightning or thunder damage, you may manifest this power as
a reaction. For this saving throw only, if you fail, you take
only half damage from the effect. If you succeed, you take
no damage.

\DndPowerHeader%
    {Scrying, Psionic\label{pwr:scrying_psionic}}
    {5th-level Prescience}
    {10 minutes}
    {Self}
    {MB 5, PD 9}
    {Concentration, up to 10 minutes}
    {None}
As the \spell{scrying} spell, except as noted
here. The power works across the planes of existence. In addition,
instead of creating an invisible sensor which appears as a
luminous orb, an ethereal form of yourself appears at the
target's location, scarcely detectable to the naked eye.
You, however, must succeed immediately on a Intelligence (Stealth)
check to avoid detection contested by the target's passive
Wisdom (Perception). You have a +10 bonus to this check.

If you wish, you may speak through your ethereal form, however
your voice is whispery and faint.

\DndPowerHeader%
    {Self Alchemy\label{pwr:self_alchemy}}
    {3rd-level Metacreativity}
    {1 action}
    {Self}
    {MB 3, PD 5}
    {See text}
    {Mundane matter}
Aided with mundane matter, you alter your physical appearance
at the molecular level, concealing your true physical identity.
You can make changes to your physical form, including your facial
appearance, however you cannot change your apparent sex nor
present features which would be atypical for your race.

Unlike the \spell{disguise self} spell and use of a Disguise Kit,
the changes wrought by \nameref{pwr:self_alchemy} hold up to
physical inspection. Use of \nameref{pwr:detect_psionics}
and similar powers or abilities, as normal,
reveals that you are under some Metacreative psionic effect---but no more.
In addition, an observer who sees you, listens to you speak and passes
a Wisdom (Insight) check with DC equal to 10 + your psionics attack
modifier becomes only aware that something is unnatural about you.

The alteration to your appearance persists until you willingly
reverse it as a free action. It also may be dispelled when you are subject
to lightning damage. When this happens, make a Constitution saving
throw with DC equal to 8 or half the lightning damage taken
(whichever is higher). If you fail, the physical alteration is reversed.

\DndPowerHeader%
    {Sense Link\label{pwr:sense_link}}
    {1st-level Voice}
    {1 action}
    {120 feet}
    {MB 1, PD 1}
    {Concentration, to 1 minute}
    {Sight}
You target one willing creature within sight.
You perceive what the target creature perceives using its
sight, hearing, taste, or smell. Only one sense is linked,
and you cannot switch between senses with the same manifestation.

You make any skill checks involving senses, such as Wisdom
(Perception), as the target, and only within the target's
field of view. You lose your Dexterity bonus to AC while directly
sensing what the target senses if you are perceiving using
the target's sight or hearing.

Once sense link is manifested, the link persists even if the
target moves out of the range of the original manifestation
as is normally the case (but the link does not work across
planes). You do not control the target, nor can you communicate
with it by means of this power.

The strength of the target's linked sense could be enhanced
by other powers or items the target possesses, allowing you
the same enhanced sense. If you are blinded or deafened, or
suffer some other sensory deprivation, the linked creature
functions as an independent sensory organ, and provides you
the benefit of the linked sense from its perspective while
this power's duration lasts.
\augment{You can augment this power in one or
both of the following ways:
\begin{itemize}
  \item If you spend 2 additional psi dice,
        you can have the target perceive one of your senses
        instead of the other way around.
  \item If you spend 4 additional psi dice,
        you can link to a second sense of the same target.
\end{itemize}
}
\DndPowerHeader%
    {Sense Link, Forced\label{pwr:sense_link_forced}}
    {2nd-level Voice}
    {1 action}
    {120 feet}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {Sight}
As the \power{sense link} power, except you
can use this power on any creature---willing or unwilling---and
this power can't be augmented.

\DndPowerHeader%
    {Share Pain\label{pwr:share_pain}}
    {3rd-level Voice}
    {1 action}
    {Touch}
    {MB 3, PD 5}
    {Concentration, up to 1 minute}
    {Speech}
You use your Voice to convince a creature
that can hear and understand you
that your wounds are in fact its own. A creature you touch
must make a Wisdom saving throw. If they fail, a link is created
between you and that creature. You take half damage from all
attacks that deal damage to you, and the target takes the
remainder as psychic damage. If your hit point maximum is
reduced by any means, that reduction is not shared with the
target. If you are immune, resistant or have some reduction
to the type of damage dealt to you, this also applies to the
linked creature.

When this power ends, subsequent damage is no longer divided
between the target and you, but damage already shared is not
reassigned.
\augment{For every 2 additional psi dice you spend, this power's save DC increases by 1.}
\DndPowerHeader%
    {Shatter Mind Blank\label{pwr:shatter_mind_blank}}
    {5th-level Voice}
    {1 action}
    {30 feet}
    {MB 5, PD 9}
    {Instantaneous}
    {None}
Your inner Voice is an illuminating light, revealing
minds which have been hidden from you. This power can negate
the \power{psionic mind blank} power or the \spell{mind blank}
spell, affecting all creatures within 30 feet of you. You
can shatter each creature's mind blank by succeeding on a
contest between your roll of 1d20 + your psionic attack modifier
and each targets' roll of 1d20 + their psionics attack modifier
or their spellcasting attack modifier, depending on whether
a power or spell respectively gave rise to the mind blank
effect. If you succeed, the mind blank ends, allowing
you to affect the target thereafter with Voice or any other
powers and abilities.

\DndPowerHeader%
    {Shockwave\label{pwr:shockwave}}
    {1st-level Psychokinesis}
    {1 action}
    {60 feet}
    {MB 1, PD 1}
    {Instantaneous}
    {Sight}
A target in range you select is pummelled
with telekinetic force for 2d6 + 2 force damage as a shockwave
radiates out from your palm. The shockwave always damages
a target within range that you can see.

Nonmagical, unattended objects (including doors, walls, locks,
and so on) may also be damaged by this power.
\augment{\begin{itemize}
  \item For every 2 additional psi dice you spend,
        this power's damage increases by 1d6 points.
  \item For every 2 additional psi dice you spend,
        this power can affect an additional target.
        Any additional target cannot be more than 15 feet
        from another target of the power.
\end{itemize}
}
\DndPowerHeader%
    {Skate\label{pwr:skate}}
    {1st-level Spacefolding}
    {1 action}
    {Self or touch}
    {MB 1, PD 1}
    {Concentration, up to 1 minute}
    {None}
You, another willing creature, or an unattended
object can slide along solid ground as if on smooth ice. If
you manifest skate on yourself or another creature, the target
of the power retains equilibrium by mental desire alone, allowing
them to gracefully skate along the ground, turn, or stop suddenly
as desired. The skater's base movement speed increases by
15 feet.

The target can skate up or down any incline or decline they
could normally walk upon without mishap, though skating up
an incline reduces the target's speed to normal, while skating
down a decline increases their speed by an additional 15 feet.

If you manifest skate on an object, treat the object as having
only one-tenth of its normal weight for the purpose of dragging
it along the ground.

\DndPowerHeader%
    {Steadfast Perception\label{pwr:steadfast_perception}}
    {3rd-level Prescience}
    {1 action}
    {Self}
    {MB 3, PD 5}
    {Concentration}
    {None}
Your vision cannot be distracted or misled,
granting you immunity to all figments and visual deceptions
(such as invisibility), but not mental deceptions. Moreover,
your Wisdom (Perception) checks are made with advantage for
the duration of this power.

\DndPowerHeader%
    {Stillness of Mind\label{pwr:stillness_of_mind}}
    {1st-level Voice}
    {1 reaction, which you take when making a Wisdom saving throw}
    {Self}
    {MB 2, PD 1}
    {Instantaneous}
    {None}
You immediately empty your mind of all transitory
and distracting thoughts, improving your self-control. You
gain a +2 bonus on the Wisdom save which triggered this power.
\augment{For every 2 additional psi dice you spend, the bonus
to your Wisdom saving throws increases by 1.
}
\DndPowerHeader%
    {Stunning Wave\label{pwr:stunning_wave}}
    {2nd-level Voice}
    {1 action}
    {10 feet}
    {MB 2, PD 3}
    {Instantaneous}
    {None}
You generate a stunning mental wave that
instantly sweeps out from your location. All creatures you
designate within 10 feet of you (you can choose certain creatures
to be unaffected) must succeed on a Wisdom saving throw or
become dazed for until the start of their next turn.
\augment{You can augment this power in one or both of the following ways.
\begin{itemize}
  \item For every 2 additional psi dice you spend,
    this power's save DC increases by 1.
  \item For every 2 additional psi dice you spend,
    this power's range and the radius of its area
    both increase by 5 feet.
\end{itemize}
}
\DndPowerHeader%
    {Sublime Insight\label{pwr:sublime_insight}}
    {9th-level Prescience}
    {1 hour}
    {Self}
    {MB 9, PD 17}
    {Instantaneous}
    {None}
You elevate your mind to a
near-universal consciousness,
cogitating countless impressions and predictions
involving any creature you have seen before,
whether personally or by means of another power
such as \nameref{pwr:scrying_psionic}.

This process gives you an uncannily accurate vision
of the creature's nature,
activities,
and whereabouts.
When you manifest the power,
you learn the following facts about the creature.
\begin{itemize}
  \item Its name, race, alignment, and character class.
  \item A general estimate of its level and hit points.
  \item Its location (including place of residence, town,
        state, world, and plane of existence).
  \item Significant items currently in its possession.
  \item Any significant activities or actions the creature
        has undertaken in the previous 8 hours,
        including details such as locales travelled through,
        the names or races of those the creature fought,
        spells it cast,
        items it acquired,
        and items it left behind
        (including the location of those items).
  \item An instantaneous mental view of the creature's
        immediate state.
\end{itemize}

Sublime Insight can defeat spells,
powers,
and special abilities such as \spell{mind blank}
(or even a \spell{wish} spell)
that normally obscures Prescience powers.
You can attempt a Intelligence check against
a DC of 6 + the caster level of the
creator of the obscuring effect)
to defeat these sorts of otherwise impervious defences.

This power is not guaranteed to work against gods, divine beings
and other supremely powerful creatures.

\DndPowerHeader%
    {Suspend Life\label{pwr:suspend_life}}
    {6th-level Prana Bindu}
    {1 action}
    {Self}
    {MB 5, PD 11}
    {Permanent unless ended or dismissed, see text}
    {None}
Your mastery over your body allows you to
slow your metabolism to a point that you are almost in suspended
animation. Even powers that detect life or thought are incapable
of determining that you are alive.

While you are suspended, you are aware of your surroundings.
You feel the passage of one day for every year that actually
passes. Though on a slower schedule, you grow hungry after
a `day' without food (though a year passes in actuality)
and begin to suffer the effects of thirst and starvation as
appropriate.

If you take any damage, you come out of your trance 4 rounds
later. The trance can also be ended by a successful use of
dispel psionics. If you choose to dismiss the power, your
trance ends 1 minute later.

\DndPowerHeader%
    {Swarm of Crystals\label{pwr:swarm_of_crystals}}
    {2nd-level Metacreativity}
    {1 action}
    {Self (15-foot cone)}
    {MB 2, PD 3}
    {Instantaneous}
    {Mundane matter, Line of Effect}
Thousands of tiny crystal shards spray forth
in an arc from your hand. These razor-like crystals slice
everything in their path. Any creature caught in the cone
takes 4d4 points of slashing damage.
\augment{For every additional psi die you spend, this power's
damage increases by 1d4.
}
\DndPowerHeader%
    {Swiftsteed\label{pwr:swiftsteed}}
    {2nd-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 2, PD 3}
    {Until the end of your current turn}
    {None}
Your body more efficiently converts its anaerobic
reserves of energy into a swift, immediate burst of speed.
When you manifest this power as a bonus action, your base
movement speed is doubled until the end of your turn.

\DndPowerHeader%
    {Teleport, Psionic\label{pwr:teleport_psionic}}
    {6th-level Spacefolding}
    {1 action}
    {10 feet}
    {MB 7, PD 11}
    {Instantaneous}
    {Sight}
This power allows you to transport yourself to another location
on the same plane of existence as you.
You must transport yourself,
but may also choose up to four other willing creatures (or one object)
that you can see within range.
If you target an object, it must be able to fit entirely inside
a 10-foot cube, and it can't be held or carried by an unwilling creature.

The destination you choose to teleport to must be familiar to you.
The degree of your familiarity with the location impacts
the likelihood that you end up in that location.
The DM rolls a d100 and consults the table below to resolve this.

\begin{table}[htbp]%
    \begin{DndTable}[
        width=\columnwidth,
        header=Psionic Teleportation
    ]{X X X X X}
        Familiarity & Mishap & Similar Area & Off Target & On Target \\
Very familiar & 01--05 & 06--13 & 14--24 & 25--100 \\
Seen casually & 01--33 & 34--43 & 44--53 & 54--100 \\
Viewed once & 01--43 & 44--53 & 54--73 & 74--100 \\
Description & 01--43 & 44--53 & 54--73 & 74--100 \\
False destination & 01--50 & 51--100 & --- & --- \\
    \end{DndTable}
\end{table}     

\subparagraph{Familiarity}
  `Very familiar' is a place you have been very often,
  a place you have carefully studied,
  or a place you can see when you cast the spell.
  `Seen casually' is somewhere you have seen more than once
  but with which you aren't very familiar.
  `Viewed once' is a place you have seen once,
  possibly using magic or psionics.
  `Description' is a place whose location and appearance you know
  through someone else's description, perhaps from a map.
  `False destination' is a place that doesn't exist.
  Perhaps you tried to scry an enemy's sanctum
  but instead viewed an illusion,
  or you are attempting to teleport to a familiar location
  that no longer exists.

\subparagraph{On Target}
  You and your group (or you and the target object)
  appear where you want to.

\subparagraph{Off Target}
  You and your group (or the target object) appear a random distance away
  from the destination in a random direction.
  Your distance off target is 1d10$\times$1d10 percent of the distance
  that was to be travelled.
  For example, if you tried to travel 120 miles,
  landed off target,
  and rolled a 5 and 3 on the two d10s,
  then you would be off target by 15 percent, or 18 miles.
  The DM determines the direction off target randomly
  by rolling a d8 and designating
  1 as north,
  2 as northeast,
  3 as east,
  and so on around the points of the compass.
  If you were teleporting to a coastal city and wound up 18 miles out at sea,
  you could be in trouble.

\subparagraph{Similar Area}
  You and your group (or the target object) wind up in a different area
  that's visually or thematically similar to the target area.
  If you are heading for your home monastery,
  you might end up in the lodgings of another psionicist
  or a monk's residence that is visually similar to your monastery.
  Generally, you appear in the closest similar place,
  but since the power has no range limit,
  you could conceivably wind up anywhere on the plane.

\subparagraph{Mishap}
  The power's strain on your mind results in a difficult journey.
  Each teleporting creature (or the target object) takes 3d10 psychic damage,
  and the DM rerolls on the table to see where you wind up
  (multiple mishaps can occur, dealing damage each time).

\DndPowerHeader%
    {Thicken Skin\label{pwr:thicken_skin}}
    {1st-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 1, PD 1}
    {Concentration, up to 10 minutes}
    {None}
Your skin or natural armour thickens and spreads
across your body, providing a +2 bonus to your AC.
\augment{You can augment this power in one
or both of the following ways.
\begin{itemize}
  \item For every 4 additional psi dice you spend,
    the AC bonus increases by 1.
  \item If you spend 3 additional psi dice,
    you can manifest this power as a reaction to being hit.
\end{itemize}
}
\DndPowerHeader%
    {Third Eye\label{pwr:third_eye}}
    {5th-level Prescience}
    {1 action}
    {Self}
    {MB 5, PD 9}
    {Concentration, up to 1 minute}
    {None}
Your vision awakens to those that were hitherto
concealed from you. You gain \emph{truesight} out to 120 feet.

\DndPowerHeader%
    {Tidal Disruption\label{pwr:tidal_disruption}}
    {5th-level Spacefolding}
    {1 action}
    {60 feet}
    {MB 4, PD 9}
    {Instantaneous}
    {Sight}
In a fleeting moment, you aggressively mould the fabric of space and time
and expose a target you can see to extreme tidal forces.
The target must make a Strength saving throw,
taking 10d6 bludgeoning damage on a failed save, or half as much on a success.
\augment{For every additional psi die you spend,
this power's damage increases by 1d6.
For each extra 2d6 points of damage,
this power's save DC increases by 1.
}
\DndPowerHeader%
    {Time Warp\label{pwr:time_warp}}
    {3rd-level Spacefolding}
    {1 action}
    {Touch}
    {MB 3, PD 5}
    {1 round per psionic threshold}
    {None}
A creature of Medium size or smaller you
touch when manifesting this power makes a Wisdom saving throw.
If they fail, they move forward in time for a number of rounds
equal to your psionic threshold. In effect, the target seems
to disappear in a shimmer of silver energy, then reappear
after the duration of this power expires. The target reappears
in exactly the same orientation and condition as before. From
the target's point of view, no time has passed at all.

In each round of the power's duration, on what would have
been the target's turn, it can attempt a Wisdom saving throw.
Success allows the target to return and the power ends. When
the target reappears---whether by succeeding on the save or
the power's duration expiring---the target can act normally
on their next turn.

If the space from which the target departed is occupied upon
their return to the time stream, they appear in the closest
unoccupied space, still in their original orientation. Determine
the closest space randomly if necessary.
\augment{You can augment this power in one or
both of the following ways.
\begin{itemize}
  \item For every 2 additional psi dice you spend,
    you can affect a creature of one size category larger.
  \item For every 2 additional psi dice you spend,
    this power can affect an additional target.
    Any additional target cannot be more than
    15 feet from another target of the power.
\end{itemize}
}
\DndPowerHeader%
    {Timeless Body\label{pwr:timeless_body}}
    {9th-level Spacefolding}
    {1 action}
    {Self}
    {MB 9, PD 17}
    {Concentration, up to 1 minute}
    {None}
You carve out a isolated pocket in time,
rendering your body impervious to the outside world. While
this power lasts, you are invulnerable to all damage and the
effects of all attacks, spells, powers and environmental conditions
(whether harmful or helpful).

\DndPowerHeader%
    {Tornado\label{pwr:tornado}}
    {9th-level Psychokinesis}
    {1 action}
    {120 feet}
    {MB 9, PD 17}
    {Instantaneous}
    {Sight}
You induce the formation of a slender vortex
of fiercely swirling air. When you manifest it, a vortex of
air visibly and audibly snakes out from your outstretched
hand, originating at a point you can see in range.
Alternatively,
if you want to aim the vortex at a specific creature you can
see in range, you can make a psionics attack to strike the
creature. If you succeed, direct contact with the vortex deals
8d6 bludgeoning damage to the creature.

Regardless of your choice,
all creatures (including the one possibly damaged
by direct contact) within a cylinder of radius
40 feet and height 100 feet are picked up and violently dashed
about, dealing 17d6 bludgeoning damage to each one. Creatures
that make a successful Dexterity save take half damage.

After being dashed about, each creature that was affected
finds itself situated in a new space 1d4 times 10 feet away
from its original space in a random direction. Walls and other
barriers can restrict this relocation; in such a case, the
creature ends up adjacent to the barrier.

\DndPowerHeader%
    {Touchsight\label{pwr:touchsight}}
    {3rd-level Prana Bindu}
    {1 action}
    {Self}
    {MB 3, PD 5}
    {Concentration, up to 1 minute}
    {None}
You generate a subtle telekinetic field of
mental contact, allowing you to `feel' your surroundings
even in total darkness or when your sight would otherwise
be obscured by your physical environment. Your touchsight
field emanates from you out to 60 feet. You ignore invisibility,
darkness, and concealment, though you must have line of sight
to a creature or an object to discern it.

You do not need to make Wisdom (Perception) checks to notice
creatures; you can detect and pinpoint all creatures within
60 feet. In many circumstances, comparing your regular senses
to what you learn with touchsight is enough to tell you the
difference between visible, invisible, hiding, and concealed
creatures.
\augment{For every 2 additional psi dice you spend, the radius
of your touchsight field increases by 10 feet.
}
\DndPowerHeader%
    {Tower of Power\label{pwr:tower_of_power}}
    {5th-level Voice}
    {1 reaction, which you take when you or an ally is targeted by a Voice or mind-affecting power}
    {Self (15-foot sphere)}
    {MB 4, PD 9}
    {Concentration, until the start of your next turn}
    {None}
You generate a bastion of thought so strong
that it offers protection to you and all creatures around
you, improving the self-control of all. You and all creatures
you choose within 15 feet of you can add an extra 2d6 to saving
throws against all Voice powers and powers that affect one's
mind. The power lasts until the start of your next turn.
\augment{For every additional psi die you spend, this power's
duration increases by 1 round.
}
\DndPowerHeader%
    {Trace Teleport\label{pwr:trace_teleport}}
    {4th-level Prescience}
    {1 action}
    {Self (60-foot sphere)}
    {MB 3, PD 7}
    {Instantaneous}
    {None}
You can trace the destination of any psionic or magical
teleportation made by others within a 60-foot radius from
you and that occurred the last minute.

You know the direction and distance the individuals travelled
as if you had casually seen the location. This power does
not grant you any information on the conditions at the other
end of the trace beyond the mental coordinates of the location.
\augment{If you spend 2 additional psi dice, this power's range
increases to 120 feet.
}
\DndPowerHeader%
    {Uncanny Reach\label{pwr:uncanny_reach}}
    {2nd-level Prana Bindu}
    {1 bonus action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {None}
Your uncanny ability to flex and contort your body allows you
to strike targets ordinarly unreachable.
While concentrating on this power, your reach with unarmed attacks
increases by 5 ft.

\DndPowerHeader%
    {Unrelenting Voice\label{pwr:unrelenting_voice}}
    {3rd-level Voice}
    {1 action}
    {Self (30-feet cone)}
    {MB 3, PD 5}
    {Instantaneous}
    {Speech$^*$, Line of Effect}
Your Voice bursts forth from you as tidal
wave of raw force, knocking creatures down. Any creature that
lies within a 30-foot cone centred on yourself must make a
Dexterity or Strength saving throw (their choice), taking
8d4 force damage on a failed saving throw or half as much
on a successful roll. In addition, each target that failed
the save is pushed 10 feet back and knocked prone.
$^*$Creatures need not hear and understand you to be
affected by your Voice.
\augment{For every additional psi die you spend, this power's
damage increases by 1d4.
}
\DndPowerHeader%
    {Vigour\label{pwr:vigour}}
    {1st-level Prana Bindu}
    {1 action}
    {Self}
    {MB 1, PD 1}
    {1 hour}
    {None}
You suffuse yourself with power, gaining
7 temporary hit points.
\augment{For every additional psi dice you spend, the number
of hit points you gain increases by 5.
}
\DndPowerHeader%
    {Wall Walker\label{pwr:wall_walker}}
    {2nd-level Spacefolding}
    {1 action}
    {Self}
    {MB 2, PD 3}
    {Concentration, up to 1 minute}
    {None}
You reverse the direction of gravity in your
immediate vicinity, allowing you to walk on vertical surfaces
or even traverse ceilings (you need not make any ability checks
to traverse these surfaces). Because of the need to keep at
least one foot in contact with the wall or ceiling at all
times, you cannot jump or take the dash action, and all walls
and ceilings walked on in this way count as difficult terrain.

\DndPowerHeader%
    {Weapon of Energy\label{pwr:weapon_of_energy}}
    {4th-level Psychokinesis}
    {1 action}
    {Touch}
    {MB 4, PD 7}
    {Until the end of your next turn}
    {None}
You can manifest this power to energise a
weapon you are holding. The weapon deals an extra 4d8 points
of cold, lightning, fire or thunder damage (as chosen by you
at the time of manifestation) on a successful hit
while the power remains active.

This power can be manifested on a weapon that is magic or
otherwise already deals damage the aforementioned types of
damage, and if the weapon already deals the same type of damage
as the power, the effects stack. If this power is manifested
on a weapon already benefiting from the effect of the power,
the newer manifestation supersedes the older manifestation.

