% P5, PK5
\DndPowerHeader%
  {Adapt Body}
  {5th-level Prana Bindu}
  {1 action}
  {Self}
  {MB 4, PD 9}
  {Concentration, up to 1 hour}
Your body automatically adapts to hostile environments.
You can adapt to underwater, extremely hot, extremely cold,
or airless environments, allowing you to survive
as if you were a creature native to that environment.
You can breathe and move (though penalties to movement and attacks,
if any for a particular environment, remain),
and you take no damage simply from being in that environment.
You need not specify what environment you are adapting to
when you manifest this power;
simply activate it,
and your body will instantly adapt to any hostile environment
as needed throughout the duration.

You can somewhat adapt to extreme environmental features such as acid,
lava, fire, and lightning.
Any environmental feature that normally directly deals
1 or more dice of damage per round
deals you only half the usual amount of damage.
In addition,
you have advantage on Constitution saving throws to maintain
concentration on powers if damage or a hazardous effect from the
extreme environment prompted the save.

% P
\DndPowerHeader%
  {Attraction}
  {1st-level Voice}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 hour}
You plant a compelling attraction in the mind of the target.
The attraction can be toward a particular person or an object.

The target makes a Wisdom saving throw.
If the target fails, they will take reasonable steps to meet,
get close to, attend, or find the object of its implanted attraction.
Otherwise, the power has no effect.

For the purpose of this power, `reasonable' means that, while attracted,
the target doesn't suffer from blind obsession.
They will act on this attraction only when not engaged in combat.
The target won't perform obviously suicidal actions.
They can still recognize danger but will not flee
unless the threat is immediate.

If you make the target feel an attraction to yourself,
you can't command them indiscriminately,
although they will be willing to listen to you (even if they disagree).

This power grants you advantage on any social skill checks
you make involving the target.
\augment{For every 2 additional psi dice you spend,
  this power's save DC increases by 1
  and the bonus on social skill checks increases by 1.}

\DndPowerHeader%
  {Aversion}
  {2nd-level Voice}
  {1 action}
  {30 feet}
  {MB 2, PD 3}
  {Concentration, up to 1 hour}
Your Voice plants a powerful aversion in the mind of the creature
you can see in range.
If the object of the implanted aversion is an individual
or a physical object,
the target will prefer not to approach within 30 feet of it.
If it is a word,
they will try not to utter it;
if it is an action,
they will not willingly attempt to perform it;
and if it is an event,
they will not willingly attend it.
The subject will take reasonable steps to avoid the object of its aversion,
but will not put themselves in jeopardy by doing so.

If the subject is forced into taking an action they have an aversion to,
they have disadvantage on any attack rolls,
ability checks,
or skill checks involved.
\augment{For every 2 additional psi dice you spend,
  this power's save DC increases by 1
  and the duration increases by 1 hour.}

\DndPowerHeader%
  {Banishment, Psionic}
  {4th-level Spacefolding}
  {1 action}
  {120 feet}
  {MB 4, PD 7}
  {Instantaneous}
As the \spell{banishment} spell, except as noted here.
\augment{For every 3 additional psi dice you spend,
  you can target one additional creature.}

\DndPowerHeader%
  {Bestow Power}
  {2nd-level Voice}
  {1 action}
  {20 feet}
  {MB 2, PD 3}
  {Instantaneous}
You link your mind with another psionic creature's mind,
creating a brief conduit through which mental energy can be shared.
When you manifest this power,
the subject gains up to 2 psi dice.
You can transfer psi dice to a subject up to their psionic threshold.
\augment{For every 3 additional psi dice you spend,
the subject gains two additional psi dice.}

\DndPowerHeader%
  {Biofeedback}
  {2nd-level Prana Bindu}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
    You can toughen your body against wounds,
    lessening their impact.
    During the duration of this power, all incoming damage
    from separate sources is reduced by 2.
\augment{For every 3 additional psi dice you spend,
the amount of damage reduced increases by 1.}

% PK1
\DndPowerHeader%
  {Bite of the Wolf}
  {1st-level Prana Bindu}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
  You temporarily alter your genomic makeup
  such that your posture becomes stooped forward,
  and you grow a muzzle complete with fangs.
  You gain one bite attack each round which
  can be used as a bonus action or as a replacement
  for one of your attacks.
  Treat the bite as a melee weapon attack.
  The bite deals 1d8 piercing damage
  (assuming you are a Medium creature)
  when it hits.
  Your bite can be affected by
  powers, spells, and effects
  that enhance or improve weapons.
  
  If you are not a Medium creature,
  your bite attack's base damage varies as follows:
  Tiny 1d4; Small 1d6; Large 2d6; Huge 2d8;
  Gargantuan 4d6.
  
  Based on your psi knight level,
  your bite increases in ferocity as noted here:
  at 5th level your bite deals an extra 1d8 points of damage,
  at 10th level an extra 2d8,
  at 15th level an extra 3d8,
  and at 20th level an extra 4d8 points.

\DndPowerHeader%
  {Blow Up Object With Mind}
  {1st-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 1, PD 1}
  {Instantaneous}
Your terrifying mental ability can cause matter to
wrench itself apart. 
Choose an object within range.
The object can be carried or worn by a creature.
Make a psionics attack roll against the object.
The AC is determined by the size of object, shown below.

If the attack hits, the object explodes.
Any creature within 10 feet of the object must make
a Dexterity saving throw.
If they fail,
they take bludgeoning damage equal to
the damage shown in the table below,
as dependent on the object's size.
If the object was being worn or carried by a creature,
that creature has disadvantage on the saving throw.
\augment{For every 2 additional psi dice you spend,
  roll one extra die using the same damage die as
  given for the object's size.}

\begin{table}[htbp]%
  \begin{DndTable}[width=\columnwidth,
                   header=Object AC and Damage]{X c c}
      Size & AC & Damage Die \\
      Tiny (bottle, pancakes)        & 11 & 2d6 \\
      Small (chest, lute)            & 13 & 2d8 \\
      Medium (barrel, chandelier)    & 15 & 2d10 \\
      Large (cart, 10x10 ft. window) & 17 & 2d12
  \end{DndTable}
\end{table}

% P2, PK2
\DndPowerHeader%
  {Body Equilibrium}
  {2nd-level Prana Bindu}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {Concentration, up to 10 minutes}
You can adjust your body's equilibrium to correspond
with any solid or liquid that you stand on.
Thus, you can walk on water, quicksand,
or even a spider's web without sinking or breaking through
(this effect does not confer any resistance to particularly sticky webs).
You can move at your normal speed,
but you cannot take the Dash action
on an non-firm surface without sinking or breaking through.

If you fall from any height while using this power,
damage from the impact is halved.

\DndPowerHeader%
  {Bolt}
  {1st-level Metacreativity}
  {1 action}
  {Touch}
  {MB 1, PD 1}
  {Concentration, up to 1 hour}
You create 2d4 crossbow bolts, arrows or sling bullets.
The ammunition dissipate upon hitting a target
or when the power ends.
The ammunition has a +1 bonus to attack and damage rolls.
\augment{For every 4 additional psi dice you spend,
  this power improves the ammunition's bonus to
  attack and damage rolls by +1,
  up to a maximum of three for each.}

% PK1
\DndPowerHeader%
  {Boots of the Demon King}
  {1st-level Prana Bindu}
  {1 action}
  {Self (5-foot radius)}
  {MB 1, PD 1}
  {Instantaneous}
Your legs briefly gain incredible strength,
and your boots crackle with lightning.
You make a kick (unarmed attack) against an
opponent within your melee range.
If the attack lands,
the target takes damage from your unarmed strike
as normal plus 2d4 lightning damage.
If the target is above half their hit point maximum,
they must succeed on a Strength saving throw or be knocked prone.
If the target is below half their hit point maximum,
they must succeed on a Strength saving throw or immediately
be sent a distance into the air equal to your Strength score.
They then fall prone and take fall damage as normal.
\augment{For every additional psi die you spend,
  the lightning damage dealt by this power increases by 1d4.}

  % P6, PK6
\DndPowerHeader%
  {Breath of Numinex}
  {6th-level Prana Bindu}
  {1 action}
  {Self (30-foot cone)}
  {MB 5, PD 11}
  {Instantaneous}
Your alter your body's chemistry in an instant,
allowing you to secrete a vitriolic acid
which you spew forth in a 30-foot cone
centred on yourself.
All creatures inside the cone must make a
Dexterity saving throw,
taking 11d6 acid damage on a failed save
or half as much on a successful save. 
\augment{For every additional psi dice you spend,
this power's damage increases by 1d6.}

\DndPowerHeader%
  {Burst}
  {1st-level Spacefolding}
  {Free action, see text}
  {Self}
  {MB 1, PD 1}
  {Until the end of your turn}
You subtly alter the space between matter
to gain a quick boost to your perceived speed.
At any point in your turn,
you may use a free action to manifest this power
and gain an extra 10 feet of base movement speed
for that turn only.

% PB2
\DndPowerHeader%
  {Chameleon}
  {1st-level Prana Bindu}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {Concentration, up to 1 hour}
  Your skin and equipment take on the color and texture
  of nearby objects,
  including floors and walls.
  You gain the ability to hide in dim light
  while the power lasts,
  any any checks you make to hide in this
  condition have advantage.
  You may also attempt to hide in normal levels
  of illumination,
  however your Dexterity (Stealth) check has disadvantage.

\DndPowerHeader%
  {Cloud Mind}
  {2nd-level Voice}
  {1 action}
  {30 feet}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
You make yourself completely undetectable to a target in range
by erasing all awareness of your presence from its mind.
If the target fails a Wisdom saving throw,
this power has the following effects.

First, you are invisible and inaudible to the creature.
It cannot even detect your presence by means of blindsight,
scent, or tremorsense.
It cannot pinpoint your location by any means.
\textit{Exception:} Creatures with truesight are still
able to discern your location,
and therefore the power has no effect on them.
  
Second, the target remains unaware of your actions,
provided you do not make any attacks or cause any obvious
or directly threatening changes in the target's environment.\
If you attack the target creature, the effect ends.
  
If you take an action that creates a sustained and obvious change
in the target's environment---for example, attacking a creature
aside from the target or moving a large or attended object
the target can see---the target immediately repeats the
saving throw against the power.
An ally of the target creature that is able to see or perceive you
can warn the target and thereby grant it another saving throw.

\DndPowerHeader%
  {Cloud Mind, Mass}
  {6th-level Voice}
  {1 action}
  {30 feet}
  {MB 6, PD 11}
  {Concentration, up to 1 minute}
As the \power{cloud mind} power,
except as noted here.
Each creature within range is affected individually.

% P2, PK 2
\DndPowerHeader%
  {Concealing Membrane}
  {2nd-level Metacreativity}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
  You weave a quasi-real membrane around yourself,
  which makes you lightly obscured.
  You remain visible within the translucent, amorphous enclosure.
  This distortion also grants you half cover
  thanks to the rippling membrane encasing your form.
  You can pick up or drop objects, easily reaching through the film.
  Anything you hold is enveloped by the membrane.
  Likewise, you can engage in melee, make ranged attacks,
  and manifest powers without hindrance.

% P1, PK1
\DndPowerHeader%
  {Conceal Thoughts}
  {1st-level Voice}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 hour}
Choose a target within range.
You protect the target's thoughts from analysis.
While the duration lasts, the target gains advantage on
Deception checks against those attempting to discern their
true intentions with Wisdom (Insight).
They also gain advantage on saving throws against any power or spell
used to read their mind (such as detect thoughts).

\DndPowerHeader%
  {Confusion, Psionic}
  {4th-level Voice}
  {1 action}
  {90 feet}
  {MB 3, PD 7}
  {Concentration, up to 1 minute}
As the \spell{confusion} spell, except as noted here.
The power targets one creature you can see within range.
\augment{For every 2 additional psi dice you spend,
  this power's save DC increases by 1,
  and the power can affect an additional target.
  Any additional target canot be more than 15 feet from another
  target of the power.}

\DndPowerHeader%
  {Control Air}
  {2nd-level Psychokinesis}
  {1 action}
  {120 feet}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
  You have some control over wind speed and direction.
  The speed of the wind within the area of this power
  can be increased or decreased by up to 10 knots.
  This power also gives you the ability to alter the direction
  of the wind by as much as 90 degrees.
  
  Powerful enough winds can cause creatures to be knocked prone.
  Creatures of size Small or smaller that are subject
  to winds between 25--45 knots
  must succeed on a DC 10 Strength saving throw or be knocked prone.
  If they wind speed is greater than 45 knots,
  this applies to Medium creatures as well.
  \augment{For every additional psi die you spend,
      you can modify the wind speed
      by an additional 10 miles per hour,
      to a maximum change in wind speed of
      50 knots.}

\DndPowerHeader%
  {Control Body}
  {4th-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 4, PD 7}
  {Concentration, up to 1 minute}
  You psychokinetically control the actions of any humanoid
  (including undead or outsiders with a humanoid physiology)
  that you can see within range.
  Control body doesn't require mental contact with the target,
  since you are actually forcing limb movements independent
  of the target's mind.
  You can force the target to stand up,
  sit down,
  walk,
  turn around,
  and so on,
  but operating the vocal cords is too difficult.
  You can also hold the target immobile,
  rendering it incapacitated.
  You cannot force the target to manifest powers,
  cast spells,
  or use any special ability that is not a function
  of just its body movements.
  If you lose sight of the target,
  the effect of this power ends.

  If you force the target to engage in combat,
  its attack bonus is equal to your
  psionics attack bonus,
  and its bonus on damage rolls is equal
  to your Intelligence bonus.
  A creature subject to this power cannot take reactions.
  The target gains no benefit to its AC from its Dexterity,
  but it does gain a bonus to its AC equal to your Intelligence bonus.
  
  Although the subject's body is under your control,
  the subject's mind is not.
  Creatures capable of taking purely mental actions
  (such as manifesting powers)
  can do so.
\augment{For every 2 additional psi dice you spend,
  this power can affect a target one size category larger.}

\DndPowerHeader%
  {Control Sound}
  {2nd-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
  You shape and alter existing sounds.
  You can target one sound, such as a person speaking or singing,
  or a group of related sounds,
  such as the patter of many raindrops or the tramp of soldiers passing by.
  A sound as quiet as a snapping finger can be controlled.
  You can substitute any sound you have heard for the target sound.
  If you attempt to exactly duplicate the voice of a specific individual,
  or an inherently terrifying sound (such as a dragon's roar),
  you must succeed on a Charisma (Deception) check with advantage
  opposed by the intended listener's Wisdom (Insight) check
  to avoid arousing suspicion.

  You can entirely muffle a noise or magnify a sound to such loudness
  that it drowns out all other conversation in the immediate area.
  
  Alternatively, you can use up the power in an instant.
  You do this by modulating a sound into a one-time destructive impetus
  that shatters nonmagical/nonpsionic,
  unattended objects of crystal, glass, ceramics, or porcelain
  (vials, bottles, flasks, jugs, mirrors, and so forth) in the area.

\DndPowerHeader%
  {Correspond}
  {4th-level Voice}
  {10 minutes}
  {Unlimited, see text}
  {MB 4, PD 7}
  {Concentration, up to 1 minute}
  You forge a mental link with a creature with which you have
  previously had physical or mental contact
  and that has an Intelligence score of 5 or greater.
  You need not have line of sight towards the target,
  nor need them to even be on the same
  plane of existence as you are.
  The subject recognizes you, and you can mentally communicate
  with it for the duration
  (though nothing forces the subject to respond to you),
  exchanging messages of twenty-five words or less once per round.

\DndPowerHeader%
  {Create Object With Mind}
  {5th-level Metacreativity}
  {1 minute}
  {30 feet}
  {MB 4, PD 9}
  {See text.}
As the \spell{creation} spell,
except as noted here.
\augment{For every 3 additional psi dice you spend,
the cube's size increases by 5 feet.}

\DndPowerHeader%
  {Create Sound}
  {1st-level Metacreativity}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
  You create a volume of sound that rises, recedes, approaches,
  or remains at a fixed place centred at a point within range.
  You choose what type of sound the power creates when manifesting it
  and cannot thereafter change its basic character.
  The volume of sound created, however, depends on your psionic threshold.
  You can produce as much noise as four normal humans per psionic threshold
  (maximum twenty humans).
  Thus, talking, singing, shouting, walking,
  marching, or running sounds can be created.
  The noise produced can be virtually any type of sound within the volume limit.
  A horde of rats running and squeaking is about the same volume as eight humans
  running and shouting.
  A roaring lion is equal to the noise from sixteen humans,
  while a roaring dire lion is equal to the noise from twenty humans.

  If you wish to create a specific message,
  up to twenty-five words can be created,
  and those words repeat over and over until the duration expires
  or the power is dismissed.
  If you attempt to exactly duplicate the voice of a specific individual
  or an inherently terrifying sound
  (such as a dragon's roar),
  you must succeed on a Deception check opposed
  by the listener's Wisdom (Insight) check to avoid arousing suspicion.
  
  Create sound can be used to bring sounds into existence that you later
  manipulate by manifesting \power{control sound}.

\DndPowerHeader%
  {Create Weapon With Mind}
  {1st-level Metacreativity}
  {1 action}
  {Touch}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
  You touch any mundane matter in front of you,
  morphing it into a weapon of your choosing
  from the weapons table (phb 146).
  The weapon is made of ordinary materials
  as appropriate for its kind.
  If you choose a projectile weapon,
  it comes with 3d6 pieces of ammunition
  of the applicable type.
  If you relinquish your grip on the weapon you called
  for 2 or more consecutive rounds,
  it loses its coherence and returns to the substance(s)
  it originated as.
\augment{You can augment this power in one or both of the follwing ways.
  \begin{itemize}
    \item For every 4 additional psi dice you spend,
      this power adds a +1 bonus to the weapon's attack and damage rolls
      (to a maximum of +3).
    \item If you spend 3 psi dice, the weapon becomes magical for the
      purpose of overcoming resistances.
  \end{itemize}}

\DndPowerHeader%
  {Crisis of Breath}
  {2nd-level Voice}
  {1 action}
  {120 feet}
  {MB 4, PD 5}
  {Concentration, up to 1 minute}
  Your Voice compels a humanoid creature you can see in range
  to purge its entire store of air
  in one explosive exhalation,
  and thereby disrupt the target's autonomic breathing cycle.
  The target's lungs do not automatically function
  again while the powers's duration lasts.

  If the target succeeds on a Wisdom save when
  crisis of breath is manifested,
  it is unaffected by this power.
  If it fails its Wisdom save,
  it can still continue to breathe by taking a standard action
  in each round to gasp for breath.
  
  An affected creature can attempt to take actions normally
  (instead of consciously controlling its breathing),
  but each round it does so,
  beginning in the round when it failed its Wisdom save,
  the target risks blacking out from lack of oxygen.
  It must succeed on a Constitution save
  at the end of any of its turns in which
  it did not consciously take a breath.
  The DC of this save increases by 1 in every consecutive
  round after the first one that goes by without a breath;
  the DC drops back to its original value
  if the target spends an action to take a breath.
  
  If a target fails its Constitution save,
  it it becomes unconscious.
  In the following round,
  it drops to 0 hit points
  but must take death saving throws.
  Curing powers or spells can revive a dying subject normally,
  so long as this power's duration has expired; 
  f the power is still in effect,
  a revived creature is still subject to Constitution saves
  in each round when it does not consciously breathe.
\augment{You can augment this power in one or more of the following ways.
\begin{itemize}
  \item If you spend 6 additional power points,
        this power can affect up to four creatures
        all within a 20-ft.-radius burst.
  \item If you spend 4 additional power points,
        this power can also affect creatures other than a humanoid,
        assuming they have a aerobic respiratory system to disrupt.
\end{itemize}}

\DndPowerHeader%
  {Cushion Fall}
  {1st-level Spacefolding}
  {1 reaction, which you take when you suffer any fall damage}
  {Self}
  {MB 1, PD 1}
  {Instantaneous}
  You recover instantly from a fall
  and can absorb some damage from falling.
  You land on your feet no matter how far you fall,
  and you take damage as if the fall were
  10 feet shorter than it actually is.
  This power affects you and anything you carry or hold
  (up to your maximum load).
\augment{For every additional psi die you spend, the power reduces
your damage as if the fall were an additional 10 feet damage.}

% PK3, P3
\DndPowerHeader%
  {Danger Sense}
  {3rd-level Prescience}
  {1 action}
  {Self}
  {MB 3, PD 5}
  {Concentration, up to 1 hour}
  You can sense the presence of danger
  before your senses would normally allow it.
  Your intuitive sense alerts you to danger from traps,
  giving you advantage on Dexterity saving throws to avoid traps
  and a +4 bonus to Armor Class when subject to any attack roll
  made by a trap.

\DndPowerHeader%
  {Deceleration}
  {1st-level Spacefolding}
  {1 action}
  {60 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
You warp space around a target in range,
hindering the target's ability to move.
The target must succeed on a Wisdom saving throw,
otherwise their speed (in every movement mode they possess) is halved.

A subsequent manifestation of deceleration on the subject
does not further decrease its speed.
\augment{For every 2 additional psi dice you spend,
  this power can affect a target one size category larger.}

\DndPowerHeader%
  {Déjà Vu}
  {1st-level Voice}
  {1 action}
  {60 feet}
  {MB 1, PD 1}
  {1 round}
The power of your Voice commands a target in range
to repeat their previous decisions.
The target must succeed on a Wisdom saving throw
or be forced to repeat the actions they took on their previous turn.
If the situation has changed in such a way that the target
can't take the same actions again
(if its foe is dead, or the target has run out of psi dice, and so on),
the target stands still and takes no actions for 1 round.
In any event, the target can still defend itself.
\augment{For every 2 additional psi dice you spend, this power's
save DC increases by 1.}

\DndPowerHeader%
  {Destiny Dissonance}
  {1st-level Prescience}
  {1 action}
  {Touch}
  {MB 1, PD 1}
  {1 round per psionic threshold}
  Your mere touch grants a creature
  a vision of the limitless potential
  of the not-yet-determined future,
  possibilities undulating like a cloth blowing in the wind.
  Unaccustomed to such a revelation,
  the creature's mind is overwhelmed.
  Make a melee psionics attack against a creature.
  If the attack hits,
  the creature takes 1d8 psychic damage
  and becomes poisoned for a number of rounds
  equal to your psionic threshold.
  \augment{For every two additional psi dice you spend,
    this power's damage increases by 1d8.}

\DndPowerHeader%
  {Detect Hostile Intent}
  {2nd-level Voice}
  {1 action}
  {30 feet}
  {MB 2, PD 3}
  {Concentration, up to 10 minutes}
  While the duration of this power lasts,
  you become aware of the presence of any creatures with hostile intent
  within 30 feet of you,
  and their direction from you
  (but not their specific location).
  The power detects active aggression,
  as opposed to vigilance.
  In addition, while this power is active you cannot be surprised
  by creatures that are susceptible to mind-affecting powers.

  While under the effect of this power,
  you can make Wisdom (Insight) checks as a free action
  against anyone you can see within 30 feet of you.
  
  The power can penetrate barriers, but 3 feet of stone,
  3 inches of common metal,
  1 inch of lead,
  or 6 feet of wood or dirt blocks it.

\DndPowerHeader%
  {Detect Psionics}
  {1st-level Prescience}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {Concentration, up to 10 minutes}
For the power's duration,
you sense the presence of psionics within 30 feet of you.
If you sense psionics in this way,
you can use your action to see a faint aura around
any visible creature or object in the area that bears psionic effects,
and you learn the discipline of the effect, if any.

The power can penetrate most barriers, but is blocked by
1 foot of stone,
1 inch of common metal,
a thin sheet of lead,
or 3 feet of wood or dirt.

\DndPowerHeader%
  {Detect Prying Eyes}
  {4th-level Prescience}
  {1 action}
  {40 feet}
  {MB 3, PD 7}
  {One day}
  You immediately become aware of any attempt to observe you
  by means of a prescience power or divination spell.
  The power's effect radiates in a 40-foot radius
  from you and moves as you move.
  You know the location of every psionic or magical sensor
  within the power's area.

  If the viewing attempt originates within the area,
  you also know the viewer's location.
  Otherwise, you and the remote viewer immediately make opposed checks.
  You make an ability check using your psionics ability modifier,
  and the remove viewer makes a check using their modifier
  for manifesting powers or casting spells if a power or spell
  respectively gave rise to the remove viewing.
  If you at least match the remote viewer's result,
  you get a visual image of the remote viewer
  and an accurate sense of the remote viewer's
  direction and distance from you.

\DndPowerHeader%
  {Demoralise}
  {1st-level Voice}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
Choose 3 hostile creatures that you can see within range.
Each creature must make a Wisdom saving throw.
If they fail, they target takes a 1d4 penalty to attack rolls and
saving throws until the power ends.
\augment{For every two additional psi dice you spend,
        you may target one additional creature.}

\DndPowerHeader%
  {Detect Thoughts}
  {2nd-level Voice}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
As the \spell{detect thoughts} spell, except as noted here.

\DndPowerHeader%
  {Diamond Bullet}
  {1st-level Metacreativity}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Instantaneous}
  Upon manifesting this power,
  you propel a diamond bullet at a target within range.
  Make a ranged psionics attack against the target.
  On a hit, the bullet deals 1d6 points of piercing damage.
\augment{For every 2 additional psi dice you spend,
  this power's damage increases by 2d6.}

  % N2, PK 2
\DndPowerHeader%
  {Dimension Swap}
  {2nd-level Spacefolding}
  {1 action}
  {60 feet}
  {MB 2, PD 3}
  {Instantaneous}
  You instantly swap positions between your current position
  and that of a designated ally in range that you can see.
  Alternatively, you can swap the positions of
  any two allies you can see that are both in range.
  This power affects creatures of Large or smaller size.
  You can bring along objects, but not other creatures.
\augment{For every 2 additional psi dice you spend, 
  this power can affect a target one size category larger.}

\DndPowerHeader%
  {Dispel Psionics}
  {3rd-level Psychokinesis}
  {1 action}
  {120 feet}
  {MB 3, PD 5}
  {Instantaneous}
  Choose one creature, object, or psionic effect within range.
  Any power of 3rd level or lower on the target ends.
  For each power of 4th level or higher on the target,
  make an ability check using your psionics ability.
  The DC equals 10 + the power's level.
  On a successful check, the power ends.
\augment{For every 2 additional psi dice you spend,
  you automatically end the effects of a power on the target
  that is one level higher.}

  % P1, PK1
\DndPowerHeader%
  {Dissipating Touch}
  {1st-level Spacefolding}
  {1 action}
  {Touch}
  {MB 1, PD 1}
  {Instantaneous}
Your mere touch can disperse the surface material of a foe or object,
sending a tiny portion of it far away.
This effect is disruptive; thus,
your successful melee psionics attack deals 1d6 points of force damage.
\augment{For every additional psi dice you spend,
  this power's damage increases by 1d6.}

\DndPowerHeader%
  {Dissolving Touch}
  {2nd-level Prana Bindu}
  {1 action}
  {Touch}
  {MB 2, PD 3}
  {Instantaneous}
  Your touch, claw, or bite is corrosive,
  and sizzling moisture visibly oozes from your
  natural weapon or hand.
  You deal 4d6 acid damage to any creature or object
  you hit with your next melee attack using the coated
  natural weapon or hand.
  You are immune to your own acid.
\augment{For every 2 additional psi dice you spend,
  this power's damage increases by 1d6.}

  \DndPowerHeader%
  {Distant Gaze}
  {2nd-level Prescience}
  {1 action}
  {See text}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
  You can see and hear a distant location
  almost as if you were there.
  You don't need to see the location
  nor have line of effect to it,
  but the locale must be known;
  that is, it must be
  a place familiar to you or an obvious one
  proximate to you,
  such as behind a nearby door,
  around a nearby corner,
  or in a grove of local trees.
  Once you have selected the locale,
  the focus of your clairvoyant sense doesn't move,
  but you can rotate it in all directions
  to view the area as desired.
  Unlike other scrying powers,
  this power does not allow psionically or supernaturally
  enhanced senses to work through it.

  If the chosen locale is magically or psionically dark,
  you see nothing.
  If it is naturally pitch black,
  you can see in a 10-foot radius around the center
  of the power's effect or out to the extent
  of your natural darkvision.
  The power does not work across planes.

  % P1, PK1
\DndPowerHeader%
  {Distract}
  {1st-level Voice}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
Your Voice causes the mind of a target in range to wander,
distracting them.
If the target fails a Wisdom saving throw,
they have disadvantage on all Wisdom (Perception)
and Wisdom (Insight) checks until the power ends.

\DndPowerHeader%
  {Divert Teleport}
  {7th-level Spacefolding}
  {1 reaction, when you take whenever another creature
  teleports}
  {120 feet}
  {MB 6, PD 13}
  {Concentration, up to 10 minutes}
  You can bend space and time to
  divert the final destination of any teleportation attempt
  made by any creature within 120 feet of you.
  This power is manifested as a reaction to that attempt.

  You can divert the destination of both incoming and outgoing
  teleportations,
  psionic and magical.
  Whenever you use this power,
  the teleporting creature makes a Wisdom saving throw.
  If they succeed, the diversion is foiled.
  
  For the purpose of this power,
  `divert' means you choose the actual destination
  of any teleportation attempt you can affect,
  as if you yourself were teleporting to that location,
  regardless of the teleportation range
  of the effect you are diverting.
  The destination you choose must be a location
  with which you are very familiar
  or that you have studied carefully.
  
\DndPowerHeader%
  {Drain Power}
  {4th-level Voice}
  {1 action}
  {30 feet}
  {MB 4, PD 7}
  {Concentration, up to 1 minute}
Your Voice commands a target to relinquish their psionic power
reserves to you.
Choose a target that you can see within range.
The target must succeed on a Wisdom saving throw
or immediately lose 1d6 psi dice, one of which is added
to your pool of psi dice.

The target continues to lose 1d6 psi dice each round you
maintain concentration on the power and the subject remains
in range.
In addition, you must continually use your action on your turn
to use the power.
If the subject is left with 0 psi dice, the power ends.

\DndPowerHeader%
  {Empath's Understanding}
  {1st-level Voice}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
You detect the surface emotions of a creature you can see in range.
You can sense basic needs, drives, and emotions.
Thirst, hunger, fear, fatigue, pain, rage, hatred, uncertainty,
curiosity, friendliness, and many other kinds of sensations and moods
can all be perceived.

You gain a +2 bonus to any social skill check involving the target
that you make in the round when you cease concentrating on this power.
\augment{
  You can augment this power in one or both of the following ways.
  \begin{itemize}
    \item For every additional psi die you spend,
          this power's range and the radius of its area increases by 5 feet.
    \item If you spend 2 additional psi dice,
          this power's maximum duration increases to 1 hour.
  \end{itemize}
}

\DndPowerHeader%
  {Empathic Feedback}
  {4th-level Voice}
  {1 action}
  {Self}
  {MB 3, PD 7}
  {Concentration, up to 10 minutes}
Your Voice berates your attacker,
causing it to empathically share your pain and suffering.
Each time a creature hits you,
it takes damage equal to the amount it dealt to you or 5 points,
whichever is less.
This damage is empathic in nature,
so powers and abilities the attacker may have such as damage reduction
and regeneration do not lessen or change this damage.
The damage from empathic feedback has no type,
so even if you took fire damage from a creature
that has immunity to fire,
empathic feedback will damage your attacker.
\augment{For every additional psi dice you spend,
  this power's damage floor (base of 5) increases by 1.}

\DndPowerHeader%
  {Energy Bolt}
  {3rd-level Psychokinesis}
  {1 action}
  {Self (120-foot line)}
  {MB 3, PD 5}
  {Instantaneous}
  Upon manifesting this power, you choose cold, lightning,
  fire, or thunder.
  You release a powerful stroke of energy of the chosen type
  that emanates from your finger tips,
  forming a line 120 feet long and 5 feet wide.
  Each creature in the line must make a Dexterity saving throw.
  A creature takes 5d6 points of damage of the chosen type
  on a failed save,
  or half as much on a successful save.
  
  \subparagraph{Cold}
  A bolt of this energy type deals +1 point of damage per die.
  The saving throw to reduce damage from a cold bolt
  is a Constitution save instead of a Dexterity save.
  
  \subparagraph{Lightning}
  Manifesting a bolt of this energy type provides
  a +2 bonus to the save DC if the target is wearing metal armour.
  
  \subparagraph{Fire}
  A bolt of this energy type deals +1 point of damage per die.
  
  \paragraph{Thunder}
  A bolt of this energy type deals -1 point of damage per die
  but provides a +1 bonus to the save DC.
\augment{For every additional psi dice you spend,
  this power's damage increases by one die (d6).
  For each extra two dice of damage,
  this power's save DC increases by 1.}

\DndPowerHeader%
  {Energy Missile}
  {2nd-level Psychokinesis}
  {1 action}
  {120 feet}
  {MB 2, PD 3}
  {Instantaneous}
  Upon manifesting this power,
  you choose cold,
  lightning,
  fire,
  or thunder.
  You release a powerful missile of energy
  of the chosen type at up to five creatures you can see in range.
  The missile deals 3d6 points of damage of the chosen type
  to each target if you hit them with a psionics attack.
  You cannot hit the same target multiple times
  with the same manifestation of this power.

  \subparagraph{Cold}
  A missile of this energy type deals +1 point of damage per die.
  The saving throw to reduce damage from a cold missile
  is a Constitution save instead of a Dexterity save.
  
  \subparagraph{Lightning}
  Manifesting a missile of this energy type provides
  a +2 bonus to the attack roll against creatures wearing metal armour.
  
  \subparagraph{Fire}
  A missile of this energy type deals +1 point of damage per die.
  
  \subparagraph{Thunder}
  A missile of this energy type deals -1 point of damage per die
  but reduces an opponent's AC by 1 for this attack only.
\augment{For every additional psi die you spend,
  this power's damage increases by 1d6.}

\DndPowerHeader%
  {Energy Push}
  {2nd-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 2, PD 3}
  {Instantaneous}
  Upon manifesting this power, you choose cold, lightning, fire, or thunder.
  You project a solid blast of energy of the chosen type at a target in range.
  The target must make a Dexterity saving throw,
  suffering from 2d6 points of damage of the chosen type if they fail.
  
  In addition, if a subject of up to one size category larger than you
  fails a Strength saving throw,
  the driving force of the energy blast pushes it back 5 feet
  plus another 5 feet for every 5 points of damage it takes.
  
  If a wall or other solid object prevents the subject from being pushed back,
  the subject instead slams into the object and takes an extra
  2d6 points of damage from the impact (no save).
  The movement caused by energy push does not provoke attacks of opportunity.
  \subparagraph{Cold}
    A blast of this energy type deals +1 point of damage per die.
    This does not apply to the slam damage.
    The saving throw to reduce damage from a cold push
    is a Constitution save instead of a Dexterity save.
  \subparagraph{Lightning}
    Manifesting a blast of this energy type provides a +2 bonus
    to the save DC if the target is wearing metal armour.
  \subparagraph{Fire}
    A blast of this energy type deals +1 point of damage per die
    (damage from impact remains at 2d6 points).
  \subparagraph{Thunder}
    A blast of this energy type deals -1 point of damage per die
    (damage from impact remains at 2d6 points)
    but provides a +1 bonus to the save DC.
\augment{For every 2 additional psi dice you spend, this power's damage
  increases by one die (d6) and its save DC increases by 1.
  The damage increase applies to both the initial blast and any damage
  from impact with an object.}

\DndPowerHeader%
  {Energy Burst}
  {3rd-level Psychokinesis}
  {1 action}
  {Self (30-foot sphere)}
  {MB 3, PD 5}
  {Instantaneous}
Upon manifesting this power, you choose cold, lightning,
fire, or thunder.
You create an explosion of unstable energy of the chosen type
that deals radiates over a 30-foot sphere
centred on yourself.
Every creature or object within range that fails a Dexterity saving throw
takes 5d6 damage of the chosen type, or
half as much damage on a successful save.
The explosion creates almost no pressure.
Since this power extends outward from you,
you are not affected by the damage.

  \subparagraph{Cold}
  A burst of this energy type deals +1 point of damage per die.
  The saving throw to reduce damage from a cold burst
  is a Constitution save instead of a Dexterity save.
  
  \subparagraph{Lightning}
  Manifesting a burst of this energy type provides a +2 bonus
  to the save DC to creatures wearing metal armour.
  
  \subparagraph{Fire}
  A burst of this energy type deals +1 point of damage per die.
  
  \subparagraph{Thunder}
    A burst of this energy type deals -1 point of damage per die
    but provides a +1 bonus to the save DC.
\augment{For every additional psi die you spend,
  this power's damage increases by one die (d6).
  For each extra two dice of damage, this power's save DC increases by 1.}

\DndPowerHeader%
  {Energy Ray}
  {1st-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 1, PD 1}
  {Instantaneous}
Upon manifesting this power,
you choose cold, lightning, fire, or thunder.
You create a ray of energy of the chosen type that
shoots forth from your fingertip and strikes a target within range,
dealing 1d6 points of damage if you succeed on a
ranged psionics attack with the ray.
The type of damage depends on
the type of energy of the ray you manifest. 
  \subparagraph{Cold}
    A ray of this energy deals +1 point of cold damage per die.
  \subparagraph{Lightning}
    Manifesting a ray of this energy type provides a
    +3 bonus on your attack roll if the target is wearing metal armour.
  \subparagraph{Fire}
    A ray of this energy type deals +1 point of fire damage per die.
  \subparagraph{Thunder}
    A ray of this energy type deals -1 point of thunder damage per die
    but reduces an opponent's AC by 1.
\augment{For every additional psi die you spend, this power's damage
increases by 1d6.}

\DndPowerHeader%
  {Energy Transformation}
  {7th-level Prana Bindu}
  {1 action}
  {Self (30-foot line), see text}
  {MB 5, PD 13}
  {Concentration, up to 10 minutes}
  Your bodily assimilates some of the effect of an
  energy attack and converts it into a jet of plasma.
  When you manifest this power,
  the total amount of cold, fire,
  lightning or thunder damage
  from separate sources is reduced by 10,
  to a minimum of 0.
  The amount of damage that has been reduced
  is `absorbed'.
  You also have advantage on saving throws to
  maintain concentration on powers if the
  saving throw was prompted by damage of the
  aforementioned types.
  \emph{Note:} if a separate source of damage is
  reduces to zero, it does not prompt a Constitution
  saving throw to maintain concentration.
  
  Whenever you absorb damage,
  you store up the energy and can later discharge it
  as a jet of plasma.
  To discharge a ray requires a standard action.
  You can choose to fire any number of rays
  during the power's duration.
  The ray you fire does fire or lightning damage
  (you may decide on the type).
  If a ray successfully strikes its target
  (requiring a psionics ranged attack),
  the target takes damage equal to the amount of energy damage
  of you have stored,
  up to a maximum of four times your psionic threshold level.
  As long as this power remains in effect,
  you can continue to absorb energy damage and
  fire additional rays using the stored damage.

\DndPowerHeader%
  {Energy Wave}
  {7th-level Psychokinesis}
  {1 action}
  {Self (60-foot cone)}
  {MB 6, PD 13}
  {Instantaneous}
  Upon manifesting this power,
  you choose cold, lightning, fire, or thunder.
  You create a flood of energy of the chosen type
  that deals 13d6 points of damage
  to each creature and object in a 60-foot cone
  centred on yourself
  that fails a Dexterity saving throw,
  or half as much on a successful save.
  This power originates at your hand
  and extends outward in a cone.
  \subparagraph{Cold}
    A wave of this energy type deals +1 point
    of damage per die.
    The saving throw to reduce damage from a cold wave
    is a Constitution save instead of a Dexterity save.  
  \subparagraph{Lightning}
    Manifesting a wave of this energy type
    provides a +2 bonus to the save DC if the target is wearing
    metal armour.
  \subparagraph{Fire}
    A wave of this energy type deals +1 point of damage per die.
  \subparagraph{Thunder}
    A wave of this energy type deals -1 point of damage per die
    but grants a +1 bonus to the save DC.
\augment{For every additional psi dice you spend,
  this power's damage increases by 1d6.
  For each extra two dice of damage,
  this power's save DC increases by 1.}

\DndPowerHeader%
  {Envenom}
  {1st-level Prana Bindu}
  {1 bonus action}
  {Touch}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
Your saliva briefly turns into a caustic bile
which does no damage to you,
but can damage your enemies.
You may use your bonus action to coat one weapon
you are holding with the bile.
The next time you hit with that weapon,
the bile deals 2d4 acid damage.

After the hit, roll 1d10.
On a roll of 10,
the bile totally corrodes the weapon,
and it is destroyed
(unless it is a magic weapon or otherwise resistant
to damage).

\DndPowerHeader%
  {Float}
  {1st-level Spacefolding}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
You mentally support yourself in water or similar liquid.
You gain a swim speed equal to your base movement speed for
the power's duration, 10 feet using the power alone,
or use the power to boost your swim speed by 10 feet if you already have one.

\DndPowerHeader%
  {Fist of Fury}
  {3rd-level Prana Bindu}
  {1 action}
  {Self}
  {MB 3, PD 5}
  {Concentration, up to 10 minutes}
Your fists become fuelled with terrifying power.
While the power lasts,
any unarmed attack you make with your fist
scores a critical hit on a roll of
19 in addition to a 20.

\DndPowerHeader%
  {Force Screen}
  {1st-level Psychokinesis}
  {1 action}
  {Self}
  {MB 2, PD 1}
  {Concentration, up to 1 minute}
You create an invisible mobile disk of force that hovers in front of you.
The force screen provides a +2 bonus to your AC until the power ends.
\augment{For every 4 additional psi dice you spend, the bonus to your armour
class from the force screen improves by 1.}

\DndPowerHeader%
  {Fusion}
  {8th-level Prana Bindu}
  {1 action}
  {Touch}
  {MB 8, PD 15}
  {Concentration, up to 1 minute}
  You and another willing, corporeal, living creature
  of the same or smaller size fuse into one being.
  As the manifester,
  you control the actions of the fused being.
  However, you can give up this control to the other creature.
  Once you give up control,
  you cannot regain it unless the other creature relinquishes it.

  The fused being has your current hit points
  plus the other creature's current hit points.
  The fused being knows all the powers you
  and the other creature know,
  has the sum of your and the other creature's psi dice,
  has the sum of your and the other creature's spell slots,
  and knows or has prepared any spells you or the other creature possesses
  (if any).
  Likewise, all feats, racial abilities, and class features
  are pooled
  (if both creatures have the same ability,
  the fused being gains it only once).
  For each of the six ability scores,
  the fused being's score is the higher of yours
  and the other creature's,
  and the fused being also has the higher hit dice
  and psionic threshold;
  this effectively means the fused being uses
  the better saving throws,
  attack bonus,
  and skill modifiers of either member,
  and it manifests powers up to the higher of the psionic thresholds
  that you or the other creature possessed before becoming fused.
  
  You decide what equipment is absorbed into the fused being
  and what equipment remains available for use.
  These fused items are restored once the power ends.
  
  When the power ends,
  the fused being separates.
  The other creature appears in an area adjacent to you that you determine.
  If separation occurs in a cramped space,
  the other creature is expelled through the Astral Plane,
  finally coming to rest materially in the nearest empty space
  and taking 1d6 force damage
  for each 10 feet of solid material passed through.
  
  Damage taken by the fused being is split evenly
  between you and the other creature when the power ends.
  You do not leave the fusion with more hit points
  than you entered it with,
  unless you were damaged prior to the fusion
  and the fused being was subsequently healed.
  In a like manner,
  the fused being's remaining power points are split
  between you and the other creature
  (you can leave with more points than you entered with,
  as long as you don't exceed the maximum power points
  for your level and ability score).
  
  If a fused being is killed,
  it separates into its constituent creatures,
  both of which are also dead.

\DndPowerHeader%
  {Grip of Iron}
  {1st-level Prana Bindu}
  {1 bonus action or reaction, see text}
  {Self}
  {MB 1, PD 1}
  {Until the end of your current turn}
  You can improve your chances in a grapple as a bonus action,
  gaining a +3 bonus on a grapple checks until
  the end of your current turn.

  In addition, you can also manifest this power
  as a reaction to being grappled; in this case, you shrug
  off your opponent's grip with superhuman strength.
  You gain a bonus to the check to avoid being grappled.
  If you do so,
  your check must use Strength (Athletics) and not
  Dexterity (Acrobatics).
\augment{For every 3 additional psi dice you spend,
  the bonus increases by 1.}

\DndPowerHeader%
  {Hammer}
  {1st-level Prana Bindu}
  {1 bonus action}
  {Self}
  {MB 1, PD 1}
  {1 round}
This power charges your touch with the force of a sledgehammer.
Until the end of your next turn,
if you make a successful unarmed attack against any creature or object,
you use 1d8 for your damage dice.
\augment{For every additional psi dice you spend, the power's duration
increases by 1 round.}

\DndPowerHeader%
  {Identify Psionics}
  {1nd-level Prescience}
  {1 minute}
  {Touch}
  {MB 1, PD 1}
  {Instantaneous}
As the \spell{identify} spell,
except for items imbued with psionics
and creatures manifesting powers.

\DndPowerHeader%
  {Immovability}
  {4th-level Prana Bindu}
  {1 action}
  {Self}
  {MB 4, PD 7}
  {Concentration, up to 1 hour}
  You are almost impossible to move.
  Your weight does not vary;
  instead, your body adjusts itself to withstand
  immense amounts of force.
  You could conceivably do this in midair.
  You have a +10 bonus on any check or saving throw
  against being moved.
  You can't voluntarily move to a new location
  unless you stop concentrating, which ends the power.

  While under the effects of this power,
  you cannot add your Dexterity bonus to your AC;
  however, your anchored body gains damage threshold (10).
  
  You cannot make physical attacks
  or perform any other large-scale movements
  (you can make smallscale movements,
  such as breathing,
  turning your head,
  moving your eyes,
  talking, and so on).
\augment{If you spend 6 psi dice you spend,
  you can manifest this power as a reaction to being
  involuntarily moved.}

\DndPowerHeader%
  {Inertial Armour}
  {1st-level Psychokinesis}
  {1 action}
  {Touch}
  {MB 1, PD 1}
  {8 hours}
As for the \spell{mage armour} spell, except as noted.

\DndPowerHeader%
  {Inertial Dampener}
  {4th-level Psychokinesis}
  {1 action}
  {Self}
  {MB 4, PD 7}
  {Concentration, up to 10 minutes}
  You create a skin-tight psychokinetic barrier around yourself
  that resists blunt-force blows and explosions.
  You become immune to bludgeoning damage for the power's duration.

\DndPowerHeader%
  {Inflict Pain}
  {2nd-level Voice}
  {1 action}
  {30 feet}
  {MB 2, PD 3}
  {1 round}
  You Voice stabs at the mind of your foe,
  unleashing torrents of horrible agony.
  The subject must succeed on a Wisdom saving throw or
  suffer wracking pain that imposes a disadvantage on attack rolls
  and skill checks.
\augment{For every 2 additional psi dice you spend,
  this power's save DC increases by 1,
  and the power can affect an additional target.
  Any additional target cannot be more than 15 feet
  from another target of the power.}

\DndPowerHeader%
  {Leap}
  {2nd-level Prana Bindu}
  {1 bonus action}
  {Self}
  {MB , PD 3}
  {Until the end of your current turn}
Your body prepares itself to undertake an incredible feat
of agility and strength.
As a bonus action,
you can propel yourself across vast distances.
You gain a flying speed equal to your base movement speed
until the end your current turn.
For example,
if you have taken the dash action on your turn to double
your base movement speed,
the fly speed you gain would be equal to that doubled speed.
\augment{If you spend 4 additional psi dice,
  any movement with this fly speed does not provoke
  opportunity attacks.}
 
\DndPowerHeader%
  {Levitate}
  {2nd-level Spacefolding}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {Concentration, up to 10 minutes}
As the \spell{levitate} spell,
except when manifested the target can only be the manifester themselves,
not any other creature or a loose object.

\DndPowerHeader%
  {Matter Agitation}
  {1st-level Psychokinesis}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
  You can excite the structure of a non-psionic,
  non-magical object,
  heating it to the point of combustion over time.
  The agitation grows more intense in the second and third rounds
  after you manifest the power, as described below.

  \subparagraph{1st Round}
    Readily flammable material
    (paper, dry grass, tinder, torches) ignites.
    Skin reddens (1 point of damage).
  \subparagraph{2nd Round}
    Wood smolders and smokes,
    metal becomes hot to the touch,
    skin blisters (1d4 points of damage),
    hair smolders, paint shrivels, water boils.
  \subparagraph{3rd and Subsequent Rounds}
    Wood ignites, metal scorches
    (1d4 points of damage for those holding metallic objects).
    Skin burns, hair ignites (1d6 points of damage) and lead melts.

\DndPowerHeader%
  {Manipulate Creature With Mind}
  {4th-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 3, PD 7}
  {Concentration, up to 1 minute}
You can affect a creature you can see in range by
concentrating your mind upon its current status
and the status you desire, once per round.
You can perform the shove, disarm or grapple action.
Resolve these attempts as normal.
Wherever you would make a Strength (Athletics) check or attack roll,
use your psionics attack modifier for the roll.
\augment{For every additional psi die you spend,
  this power grants a +1 bonus on all rolls you make with his power to
  shove, grapple and disarm.}
  
  \DndPowerHeader%
    {Manipulate Objects With Mind}
    {3rd-level Psychokinesis}
    {1 action}
    {120 feet}
    {MB 2, PD 5}
    {Concentration, up to 1 minute}
  By focusing your mind, you are able to manipulate objects as you desire.
  Choose an object within range weighing no more than 250 pounds.
  Each turn you spend concentrating on this power,
  including the turn in which you manifest this power,
  you may move the object up to 20 feet.
  This power ends if the object is moved out of range,
  and if you cease concentration,
  the object falls or stops.

  You may drop the object and pick up another during
  the same turn as long as you don't stop concentrating
  on the power.
  You may also exert fine control on the objects you move.
  The object does not move fast enough to cause any damage
  when being rammed into other creatures or objects,
  however it can cause damage to creatures and objects
  if it is dropped onto them.
  In this case, the object or creature deals as much
  bludgeoning damage as it would take from the fall itself.
  If the object falls onto a creature,
  they must succeed on a Dexterity saving throw
  to avoid taking the damage.

  If the object you are attempting to move is being being carried, worn
  or is equipped to a creature in some way,
  the creature can prevent you from moving the object.
  If they do so, make an ability check with your
  psionics ability modifier (not psionics attack modifier)
  contested by their Strength check.
  If they win the contest, you cannot move that and
  any other object until your turn ends.
  If the contest ends in a draw, you cannot move
  that object, but you may attempt to move others.
  % no uninterrupted prong
  \augment{For every additional psi die you spend,
    the weight limit of the target increases by 25 pounds.}
  
\DndPowerHeader%
  {Mind Blank, Psionic}
  {6th-level Voice}
  {1 action}
  {Self}
  {MB 6, PD 11}
  {duration}
As the \spell{mind blank} spell, except as noted here.
Your internal Voice conceals your mind---or
the mind of one creature you touch---from
outside influence,
rendering it effectively invisible. 

\DndPowerHeader%
  {Mind Palace, Power$^*$}
  {4th-level Psychokinesis}
  {1 reaction, see text}
  {Self}
  {MB 4, PD 7}
  {1 round, see text}
  As a reaction to when you or an ally within 20 feet of you
  is targeted by an attack or subject to a harmful effect,
  you encase yourself and your allies in a
  shimmering palace of psychokinetic force.
  The palace is a sphere of radius 20 feet centred on you. 
  All damage from powers and innate talents
  taken by subjects inside the area of the intellect fortress
  is halved.
  This lowering takes place prior to the effects
  of other powers or abilities that lessen damage.
  The palace lasts until the start of your next turn.
  
  You can manifest this power instantly,
  quickly enough to gain its benefits in an emergency.
  Manifesting the power is an immediate action.
  You can use this power even when it's not your turn.

  $^*$Not to be confused with the \emph{mind palace} ability.
\augment{For every additional psi dice you spend,
this power's duration increases by 1 round.}

\DndPowerHeader%
  {Mind Thrust}
  {1st-level Voice}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Instantaneous}
You instantly deliver a massive assault on the thought pathways
of any one creature in range.
The target must succeed on an Intelligence saving throw
or take 1d10 points of psychic damage.
\augment{For every additional psi dice you spend, the power's damage
increases by 1d10.}

\DndPowerHeader%
  {Missive}
  {1st-level Voice}
  {1 action}
  {60 feet}
  {MB 1, PD 1}
  {Instantaneous}
  You send a telepathic message of up to ten words to
  any living creature within range.
  Missive is strictly a one-way exchange from you to the target.
  If you do not share a common language,
  the target `hears' meaningless mental syllables.
\augment{For every 2 additional psi dice you spend,
the power's range increases by 5 feet.}

\DndPowerHeader%
  {Object Reading}
  {2nd-level Prescience}
  {1 minute}
  {Touch}
  {MB 2, PD 3}
  {Concentration, up to 10 minutes}
  You can learn details of an inanimate object's previous owner.
  Objects accumulate psychic impressions
  left by their previous owners,
  which can be read by use of this power.
  The amount of information revealed depends
  on how long you study a particular object.

  \subparagraph{1st Minute}
    Last owner's race.
  \subparagraph{2nd Minute}
    Last owner's gender.
  \subparagraph{33d Minute}
    Last owner's age.
  \subparagraph{4th Minute}
    Last owner's alignment.
  \subparagraph{5th Minute}
    How last owner gained and lost the object.
  \subparagraph{6th+ Minute}
    Next-to-last owner's race, and so on.
  
  The power always correctly identifies the last owner of the item,
  and the original owner
  (if you keep the power active long enough).
  
  There is a 90\% chance
  that this power will successfully identify all other former owners
  in sequence,
  but there is a 10\% chance that one former owner
  will be skipped and thus not identified.
  
  This power will not identify casual users as owners
  (anyone who uses an object to attack someone
  or something is not thereafter considered a casual user).
  
  An object without any previous owners reveals no information.
  You can continue to run through a list of previous owners
  and learn details about them as long as the power's duration lasts.
  If you use this power additional times on the same object,
  the information yielded is the same
  as if you were using the power on the object for the first time.
\augment{For every additional psi die you spend,
  this power's maxmimum duration increases by 10 minutes.}

\DndPowerHeader%
  {Orient Self}
  {1st-level Prescience}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {Instantaneous}
You generally know where you are.
This power is useful to characters who end up at unfamiliar destinations
after teleporting,
using a gate,
or travelling to or from other planes of existence.
The power reveals general information about your location
as a feeling or presentiment.
The information is usually no more detailed than a summary
that locates you according to a prominent local or regional site.
Using this power also tells you what direction you are facing.

\DndPowerHeader%
  {Plane Shift, Psionic}
  {5th-level Spacefolding}
  {1 action}
  {Touch}
  {MB 4, PD 9}
  {Instantaneous}
  Your mind warps space and time,
  allowing you to move yourself
  or some other creature to another plane of existence
  or alternate dimension.
  If several willing persons link hands in a circle,
  as many as eight can be affected by the plane shift at the same time.
  Unlike the \spell{plane shift} spell,
  precise accuracy as to a particular arrival location
  on the intended plane is nigh impossible.
  When you travel to another plane of existence,
  you appear 5 to 500 miles (5d100) from your intended destination.
\augment{For every 3 additional psi dice you spend,
roll one less d100 when determining how close you arrive
to your intended destination.}

\DndPowerHeader%
  {Possible Futures}
  {5th-level Prescience}
  {1 action}
  {Self}
  {MB 4, PD 9}
  {Concentration, up to 1 minute}
  You take a hand in influencing the probable outcomes
  of your immediate environment.
  You see the many alternative branches that reality could take
  in the next few seconds,
  and with this foreknowledge you gain the ability to,
  while this power lasts,
  reroll one attack roll,
  one saving throw,
  one ability check,
  or one skill check each round.
  You must take the result of the reroll,
  even if it's worse than the original roll.
  You do not have to make another roll
  if satisfied with your original roll.

\DndPowerHeader%
  {Power Pirate}
  {6th-level Voice}
  {1 action}
  {60 feet}
  {MB 5, PD 11}
  {Concentration, up to 1 round per psionic threshold}
  You use your Voice to take over control of a power
  that was manifested by a target you can see in range
  and that must be maintained through concentration.

  Once you wrest control of the power from the subject,
  you have several options.
  \begin{itemize}
    \item Allow the power to function as normal.
    \item Keep the power targeted on the subject
          (if a personal power) but decide how the power
          fulfils its function each round.
    \item Retarget the power on yourself (if a personal power).
    \item Choose not to concentrate on the usurped power
            in the next round, ending the power at that point.
  \end{itemize}
When the duration of \power{power pirate} expires,
the power you took control of ends
(even if this would mean that the power ends earlier than normal).

\DndPowerHeader%
  {Precognition}
  {1st-level Prescience}
  {1 action}
  {Self}
  {MB 2, PD 1}
  {Concentration, up to 1 minute}
Your awareness of your immediate circumstances extends
a fraction of a second into the future,
granting you an edge over your opponents and environment.
Choose a variation from the list below.
The nature of the benefit conferred to you
depends on the chosen variant.
\subparagraph{Defensive}
  You can a +1 bonus to your AC and on all saving throws.
\subparagraph{Anticipatory}
  You gain a +1 bonus to attack rolls.
\subparagraph{Offensive}
  You gain a +2 to bonus to your damage rolls.
\augment{For every 3 additional psi dice you spend, the bonus
you have gained from a variant increaes by 1 to a maximum of 3.}

% P4, PK4
\DndPowerHeader%
  {Psi Door}
  {4th-level Spacefolding}
  {1 action}
  {500 feet}
  {MB 3, PD 7}
  {Instantaneous}
As the \spell{dimension door}, except as noted here.
\augment{If you spend 6 additional psi dice,
  you can manifest this power as a bonus action.}

\DndPowerHeader%
  {Psi Hand}
  {1st-level Psychokinesis}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
As the \spell{mage hand} spell.

\DndPowerHeader%
  {Psi Vision}
  {2rd-level Prescience}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {duration}
As the \spell{darkvision} spell.

\DndPowerHeader%
  {Psi Wall}
  {4th-level Metacreativity}
  {1 action}
  {30 feet}
  {MB 4, PD 7}
  {Concentration, up to 1 minute}
You fashion a great wall of raw material which emerges from the earth.
The wall cannot move once it is formed.
It is 1 inch thick per psionic threshold
and occupies up to one 10-foot square per psionic threshold.
Each 10-foot square of the wall has 10 hit points per inch of thickness
and damage immunity 5.
A section of the wall whose hit points drop to 0 is breached
and can be passed through.
Otherwise, if a creature tries to break through the wall,
they can do so with successful the Strength check with
DC equal to 15 + the number of inches it is thick.

The wall is susceptible to the \power{dispel psionics} power,
but it gains a +4 bonus on any check
to determine whether the wall is negated.
Spells, powers, and breath weapons cannot pass through the wall
in either direction
(though they could damage it).
The wall is opaque, and thus a creature on one side does not have
sight of for example creatures on the other side.
The wall does not block travel by Spacefolding,
such as that provided by the \power{psionic teleport} power.
  
You can form the wall into a flat, vertical plane
whose area is up to one 10-foot square per psionic threshold
or into a sphere or hemisphere
with a radius of up to 1 foot per psionic threshold.
  
The wall must be continuous and unbroken when manifested.
If its surface is interrupted by any object or creature,
the power fails.

\DndPowerHeader%
  {Psionic Golem}
  {1st-level Metacreativity}
  {1 action}
  {30 feet}
  {MB 1, PD 1}
  {Up to 1 minute}
  This power creates one 1st-level psionic golem
  (see \secref{sec:psionic_golem})
  that attacks your enemies.
  It appears where you designate and acts
  whenever you end your turn
  (it still technically acts on your turn, however).
  It attacks your opponents to the best of its ability.
  As a free action,
  you can mentally direct it not to attack,
  to attack particular enemies,
  or to perform other actions.
  The psionic golem acts normally on the last round
  of the power's duration
  and dissipates after you finish your turn.

  Psionic golems are not summoned;
  they are created on the plane you inhabit
  using raw, mundane matter.
  Thus, they are not subject to effects
  that hedge out or otherwise affect outsiders;
  they are constructs, not outsiders.
\augment{For every 3 additional psi dice you spend,
  the level of the psionic golem increases by 1.}

\DndPowerHeader%
  {Psionic Golem, Repair}
  {2nd-level Metacreativity}
  {1 action}
  {Touch}
  {MB 2, PD 3}
  {Instantaneous}
  When laying your hands upon a psionic golem
  that has at least 1 hit point remaining,
  you reknit its structure to repair damage it has taken.
  The power repairs 3d8 points of damage
  +1 point per psionic threshold.
  Constructs that are immune to psionics or magic
  cannot be repaired in this fashion.
\augment{For every 2 additional psi dice you spend,
  this power repairs an additional 1d8 hit points.}

\DndPowerHeader%
  {Psionic Step}
  {2nd-level Spacefolding}
  {1 bonus action}
  {Self}
  {MB 2, PD 3}
  {Instantaneous}
You create a brief, unstable link between two nearby locations,
allowing you to jump from one spot to another.
You teleport to an unoccupied space you can see
up to 30 feet from you.
\augment{For every 2 additional psi dice you spend,
  you can teleport an extra 10 feet.}

\DndPowerHeader%
  {Psychic Archaeology}
  {2nd-level Prescience}
  {1 hour}
  {60 feet}
  {MB 2, PD 3}
  {Concentration, up to 1 hour}
  You gain historical vision in a given location.
  Rooms, streets, tunnels, and other discrete locations
  accumulate psychic impressions left by powerful emotions
  experienced in a given area.
  These impressions offer you a picture of the location's past.

  The types of events most likely to leave
  psychic impressions are those that elicited strong emotions:
  battles and betrayals,
  marriages and murders,
  births and great pain,
  or any other event where one emotion dominates.
  Everyday occurrences leave no residue for a manifester to detect.
  
  The vision of the event is dreamlike and shadowy.
  You do not gain special knowledge of those involved in the vision,
  though you might be able to read large banners
  or other writing if they are in your language.
  
  Beginning with the most recent significant event
  at a location and working backward in time,
  you can sense one distinct event for every 10 minutes
  you maintain concentration,
  if any such events exist to be sensed.
  Your sensitivity extends into the past
  a maximum number of years equal to
  200 times your psionic threshold.

\DndPowerHeader%
  {Psychic Crush}
  {5th-level Voice}
  {1 action}
  {30 feet}
  {MB 4, PD 9}
  {Instantaneous}
Your Voice abruptly and brutally crushes the mental essence
of any one creature, debilitating its acumen.
The target must succeed on a Wisdom saving throw
or take 6d12 psychic damage.
If they succeed, they instead take 3d6 psychic damage.
\augment{For every 2 additional psi dice you spend,
  the damage on a successful save increases by 1d6.}

\DndPowerHeader%
  {Psychofeedback}
  {5th-level Prana Bindu}
  {1 action}
  {Self}
  {MB 5, PD 9}
  {1 minute}
  You can readjust your body to boost one
  physical ability score at the expense of one
  or more of the other scores.
  Select one ability score you would like to boost,
  and increase it by the same amount that you decrease
  one or more other scores.

  You can boost your
  Strength, Dexterity or Constitution score by an
  amount equal to your psionic threshold
  (or any lesser amount),
  assuming you can afford to burn your other ability
  scores to such an extent.
  
  When the duration of this power expires,
  your ability boost also ends,
  but your the ability score drain decrease
  remains until you finish a long rest.

  % PK 2, P3
\DndPowerHeader%
  {Rapid Healing}
  {3rd-level Prana Bindu}
  {1 bonus action}
  {30 feet}
  {MB 2, PD 5}
  {Instantaneous}
You mind takes control of your body's healing process,
rapidly speeding it up.
You gain hit points equal to 1d12 + your psionics ability modifier.
\augment{For every 2 additional psi dice you spend, this power
  heals an additional 1d8 points of damage.}

\DndPowerHeader%
  {Recall}
  {1st-level Prescience}
  {1 minute}
  {Self}
  {MB 1, PD 1}
  {Instantaneous}
By meditating on a subject, you can recall
natural memories and knowledge otherwise inaccessible to you.

When you fail a History, Religion, Arcana or Nature check,
you can manifest this power to, at the end of the
power's manifesting time, repeat the check.
If successful, you instantly recall
what was previously buried in your subconscious.

\DndPowerHeader%
  {Remote View Trap}
  {6th-level Prescience}
  {1 action}
  {Self}
  {MB 5, PD 11}
  {24 hours}
  When others use any means of scrying you from afar,
  your prepared trap gives them a nasty surprise.
  If the scryer fails a Wisdom saving throw
  when it attempts to scry you,
  you are undetected.
  Moreover, the would-be observer takes 8d6 lightning damage.
  If the scryer succeeds its saving throw,
  it takes only half as much damage
  and is able to observe you normally.
  
  Either way, you are aware of the attempt to view you,
  but not of the viewer or the viewer's location.

\DndPowerHeader%
  {Restore Extremity}
  {5th-level Prana Bindu}
  {1 action}
  {Touch}
  {MB 5, PD 9}
  {Instantaneous}
  You restore a severed extremity to a creature that has
  lost a digit,
  hand,
  arm,
  leg,
  or even its head.
  This power does not restore life,
  but it returns a lost extremity to a living or dead creature
  if the creature is otherwise mostly intact.
  The original extremity need not be present
  when this power is manifested;
  a new extremity is created by the power.
  If a head is restored to a body,
  the original head (if not already destroyed)
  loses all spark of identity,
  and can be considered so much dead tissue.

\DndPowerHeader%
  {Resuscitation}
  {3rd-level Voice}
  {1 action}
  {30 feet}
  {MB 3, PD 5}
  {Instantaneous}
Your Voice commands a creature back to life.
If a creature you can see within range
has died in between your previous turn
and your current turn,
you may as an action return them to life
with 1 hit point.
This power can't return to life a creature
that has died of old age,
nor can it restore any missing body parts.

\DndPowerHeader%
  {Retrieve}
  {6th-level Spacefolding}
  {1 action}
  {60 feet}
  {MB 5, PD 11}
  {Instantaneous}
  You automatically teleport an item you can see within range
  directly to your hand.
  The item can weigh up to
  10 times your psionic threshold in pounds.
  If the object is in the possession of an opponent,
  it comes to your hand if your opponent
  fails a Wisdom saving throw.
\augment{For every additional psi dice you spend,
  the weight limit of the target increases by 10 pounds.}

\DndPowerHeader%
  {Reveal Agony}
  {2nd-level Prescience}
  {1 action}
  {60 feet}
  {MB 2, PD 3}
  {Instantaneous}
  The fabric of time parts to your will,
  revealing wounds a creature in range is yet to receive.
  If the target fails a Wisdom saving throw,
  the target takes 2d6 psychic damage as the future
  impinges briefly on the present.
\augment{For every additional psi dice you spend, 
  this power's damage increases by 1d6 points.
  For each extra 2d6 points of damage,
  this power's save DC increases by 1.}

  % P7, PK3
\DndPowerHeader%
  {Sacrificial Shell}
  {3rd-level Metacreativity}
  {1 reaction, which you take when making a saving throw
    against certain damage types, see text}
  {Self}
  {MB 3, PD 5}
  {Instantaneous}
You instantly weave a protective shell around you
which absorbs damage and then falls of.
When you make a saving throw against an effect
which would deal fire, cold, lightning or thunder damage,
you may manifest this power as a reaction.
For this saving throw only,
if you fail, you take only half damage from the effect.
If you succeed, you take no damage.

\DndPowerHeader%
  {Scrying, Psionic}
  {5th-level Prescience}
  {10 minutes}
  {Self}
  {MB 5, PD 9}
  {Concentration, up to 10 minutes}
As the \spell{scrying} spell, except as noted here.
The power works across the planes of existence.
In addition,
instead of creating an invisible sensor which appears
as a luminous orb,
an ethereal form of yourself appears at the target's location,
scarcely detectable to the naked eye.
You,
however,
must succeed immediately on a Intelligence (Stealth) check
to avoid detection contested by the target's passive
Wisdom (Perception).
You have a +10 bonus to this check.

If you wish,
you may speak through your ethereal form,
however your voice is whispery and faint.

\DndPowerHeader%
  {Sense Link}
  {1st-level Voice}
  {1 action}
  {120 feet}
  {MB 1, PD 1}
  {Concentration, to 1 minute}
  You target one willing creature within sight.
  You perceive what the target creature perceives using its sight,
  hearing, taste, or smell.
  Only one sense is linked,
  and you cannot switch between senses with the same manifestation.

  You make any skill checks involving senses,
  such as Wisdom (Perception), as the target,
  and only within the target's field of view.
  You lose your Dexterity bonus to AC while
  directly sensing what the target senses.
  
  Once sense link is manifested, the link persists
  even if the target moves out of the range
  of the original manifestation
  (but the link does not work across planes).
  You do not control the target,
  nor can you communicate with it by means of this power.
  
  The strength of the target's linked sense could be enhanced
  by other powers or items,
  allowing you the same enhanced sense.
  If you are blinded or deafened, or suffer some other sensory deprivation,
  the linked creature functions as an independent sensory organ,
  and provides you the benefit of the linked sense from its perspective
  while this power's duration lasts.
\augment{You can augment this power in one or
both of the following ways:
\begin{itemize}
  \item If you spend 2 additional psi dice,
        you can have the target perceive one of your senses
        instead of the other way around.
  \item If you spend 4 additional psi dice,
        you can link to a second sense of the same target.
\end{itemize}
}

\DndPowerHeader%
  {Sense Link, Forced}
  {2nd-level Voice}
  {1 action}
  {60 feet}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
As the \power{sense link} power,
except you can yse this power on any creature---willing or
unwilling---and this power can't be augmented.

\DndPowerHeader%
  {Share Pain}
  {3rd-level Voice}
  {1 action}
  {Touch}
  {MB 3, PD 5}
  {Concentration, up to 1 minute}
  You use your Voice to convince a creature that your wounds are
  in fact its own.
  A creature you touch must make a Wisdom saving throw.
  If they fail, a link is created between you and that creature.
  You take half damage from all attacks that deal damage to you,
  and the target takes the remainder as psychic damage.
  If your hit point maximum is reduced by any means,
  that reduction is not shared with the target.
  If you are immune, resistant or have some reduction
  to the type of damage dealt to you,
  this also applies to the linked creature. 
  
  When this power ends,
  subsequent damage is no longer divided between the target and you,
  but damage already shared is not reassigned.

  If you and the subject move farther away from each other
  than close range, the power ends.
\augment{For every 2 additional psi dice you spend,
  this power's save DC increases by 1.}

\DndPowerHeader%
  {Shatter Mind Blank}
  {5th-level Voice}
  {1 action}
  {30 feet}
  {MB 5, PD 9}
  {Instantaneous}
  Your Voice is an illuminating light,
  revealing minds which have been hidden from you.
  This power can negate the \power{psionic mind blank} power
  or the \spell{mind blank} spell,
  affecting all creatures within 30 feet of you
  if they fail a Wisdom saving throw.
  If the target fails its save,
  you can shatter the mind blank by succeeding on a
  contest between your roll of
  1d20 + your psionic attack modifier
  and each targets roll of 
  1d20 + their psionics attack modifier or
  their spellcasting attack modifier,
  depending on whether a power or spell respectively
  gave rise to the mind blank effect.
  If you succeed,
  the psionic mind blank ends,
  allowing you to affect the target thereafter
  with Voice or any other powers and abilities.

\DndPowerHeader%
  {Shockwave}
  {2nd-level Psychokinesis}
  {1 action}
  {60 feet}
  {MB 2, PD 3}
  {Instantaneous}
A target in range you select is pummelled with telekinetic force
for 1d6 force damage as a shockwave radiates out from your palm.
The shockwave always affects a target within range that you can see,
even if the target has cover, but not total cover.

Nonmagical, unattended objects
(including doors, walls, locks, and so on)
may also be damaged by this power.
\augment{You can augment this power in one or both of the following ways.
\begin{itemize}
  \item For every 2 additional psi dice you spend,
        this power's damage increases by 1d6 points.
  \item For every 2 additional psi dice you spend,
        this power can affect an additional target.
        Any additional target cannot be more than 15 feet
        from another target of the power.
\end{itemize}}

\DndPowerHeader%
  {Skate}
  {1st-level Spacefolding}
  {1 action}
  {Self or touch}
  {MB 1, PD 1}
  {Concentration, up to 1 minute}
  You, another willing creature, or an unattended object
  can slide along solid ground as if on smooth ice.
  If you manifest skate on yourself or another creature,
  the target of the power retains equilibrium by mental desire alone,
  allowing them to gracefully skate along the ground,
  turn, or stop suddenly as desired.
  The skater's base movement speed increases by 15 feet.
  As with any effect that increases speed,
  this power affects the target's maximum jumping distance.

  The target can skate up or down any incline or decline\
  they could normally walk upon without mishap,
  though skating up an incline reduces the target's speed to normal,
  while skating down a decline increases their speed
  by an additional 15 feet.
  
  If you manifest skate on an object,
  treat the object as having only one-tenth of its normal weight
  for the purpose of dragging it along the ground.

  % Pk 4
\DndPowerHeader%
  {Steadfast Perception}
  {4th-level Prescience}
  {1 action}
  {Self}
  {MB 4, PD 7}
  {Concentration}
  Your vision cannot be distracted or misled,
  granting you immunity to all figments and visual deceptions
  (such as invisibility),
  but not mental deceptions.
  Moreover, your Wisdom (Perception) checks
  are made with advantage for the duration of this power.

  % P1, PK1
\DndPowerHeader%
  {Stillness of Mind}
  {1st-level Voice}
  {1 reaction, which you take when making a Wisdom saving throw}
  {Self}
  {MB 2, PD 1}
  {Instantaneous}
You empty your mind of all transitory and distracting thoughts,
improving your self-control.
You gain a +2 bonus on the Wisdom save which triggered this power.
\augment{For every 2 additional psi dice you spend, the bonus to your
  Wisdom saving throws increases by 1.}

\DndPowerHeader%
  {Stunning Wave}
  {2nd-level Voice}
  {1 action}
  {10 feet}
  {MB 2, PD 3}
  {Instantaneous}
  You generate a stunning mental wave that instantly sweeps out from your location.
  All creatures you designate within 10 feet
  (you can choose certain creatures to be unaffected)
  must succeed on a Wisdom saving throw or become dazed for until the start of
  their next turn.
\augment{You can augment this power in one or both of the following ways.
\begin{itemize}
  \item For every 2 additional psi dice you spend,
        this power's save DC increases by 1.
  \item For every 2 additional psi dice you spend,
        this power's range and the radius of its area both increase by 5 feet.
\end{itemize}}

\DndPowerHeader%
  {Sublime Insight}
  {9th-level Prescience}
  {1 hour}
  {Self}
  {MB 9, PD 17}
  {Instantaneous}
  You elevate your mind to a near-universal consciousness,
  cogitating countless impressions and predictions
  involving any creature you have seen before,
  whether personally or by means of another power
  such as \power{psionic scrying}.

  This process gives you an uncannily accurate vision
  of the creature's nature,
  activities,
  and whereabouts.
  When you manifest the power,
  you learn the following facts about the creature.
  \begin{itemize}
    \item Its name, race, alignment, and character class.
    \item A general estimate of its level and hit points.
    \item Its location (including place of residence, town,
          country, world, and plane of existence).
    \item Significant items currently in its possession.
    \item Any significant activities or actions the creature
          has undertaken in the previous 8 hours,
          including details such as locales traveled through,
          the names or races of those the creature fought,
          spells it cast,
          items it acquired,
          and items it left behind
          (including the location of those items).
    \item An instantaneous mental view of the creature's
          immediate state.
  \end{itemize}

  Sublime Insight can defeat spells,
  powers,
  and special abilities such as \spell{mind blank}
  (or even a wish spell)
  that normally obscures Prescience powers.
  You can attempt a check---adding your
  Intelligence modifier to a d20 roll---against
  a DC of 6 + the caster level of the
  creator of the obscuring effect)
  to defeat these sorts of otherwise impervious defences.

  This power is not guaranteed to work against gods, divine beings
  and other supremely powerful beings.

% PK6, P6
\DndPowerHeader%
  {Suspend Life}
  {6th-level Prana Bindu}
  {1 action}
  {Self}
  {MB 5, PD 11}
  {Permanent unless ended or dismissed, see text}
  Your mastery over your body allows you to slow your
  metabolism to a point
  that you are almost in suspended animation.
  Even powers that detect life or thought are
  incapable of determining that you are alive.

  While you are suspended,
  you are aware of your surroundings.
  You feel the passage of one day
  for every year that actually passes.
  Though on a slower schedule,
  you grow hungry after a `day' without food
  (though a year passes in actuality)
  and begin to suffer the effects of
  thirst and starvation as appropriate.
  
  If you take any damage,
  you come out of your trance 4 rounds later.
  The trance can also be ended by a
  successful use of dispel psionics.
  If you choose to dismiss the power,
  your trance ends 1 minute later.

\DndPowerHeader%
  {Swarm of Crystals}
  {2nd-level Metacreativity}
  {1 action}
  {Self (15-foot cone)}
  {MB 2, PD 3}
  {Instantaneous}
  Thousands of tiny crystal shards spray forth in an arc from your hand.
  These razor-like crystals slice everything in their path.
  Any creature caught in the cone takes 3d4 points of slashing damage.
\augment{For every additional psi dice you spend,
  this power's damage increases by 1d4.}

\DndPowerHeader%
  {Swiftsteed}
  {2nd-level Prana Bindu}
  {1 bonus action}
  {Self}
  {MB 2, PD 3}
  {Until the end of your current turn}
  Your body more efficiently converts its anaerobic
  reserves of energy into a swift, immediate burst of speed.
  When you manifest this power as a bonus action,
  your movement speed is doubled until the end
  of your turn.

  % PK1, PB1
\DndPowerHeader%
  {Thicken Skin}
  {1st-level Prana Bindu}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {Concentration, up to 10 minutes}
  Your skin or natural armor thickens
  and spreads across your body,
  providing a +1 bonus to your AC.
\augment{You can augment this power in one
  or both of the following ways.
\begin{itemize}
  \item For every 4 additional power points you spend,
    the AC bonus increases by 1.
  \item If you spend 6 additional power points,
    you can manifest this power as a reaction to being hit.
\end{itemize}}

\DndPowerHeader%
  {Third Eye}
  {5th-level Prescience}
  {1 action}
  {Self}
  {MB 5, PD 9}
  {Concentration, up to 1 minute}
Your vision awakens to those that were hitherto
concealed from you.
You gain \emph{truesight} out to 120 feet.

\DndPowerHeader%
  {Time Warp}
  {3rd-level Spacefolding}
  {1 action}
  {Touch}
  {MB 3, PD 5}
  {1 round per psionic threshold}
  A creature of Medium size or smaller
  you touch when manifesting this power makes a Wisdom saving throw.
  If they fail, they move forward in time for a number of rounds
  equal to your psionic threshold.
  In effect, the target seems to disappear in a shimmer
  of silver energy,
  then reappear after the duration of this power expires.
  The target reappears in exactly the same
  orientation and condition as before.
  From the target's point of view,
  no time has passed at all.

  In each round of the power's duration,
  on what would have been the target's turn,
  it can attempt a Wisdom saving throw.
  Success allows the target to return and the power ends.
  The target can then act normally on its next turn,
  or in any case when the power ends.
  
  If the space from which the target departed is occupied
  upon their return to the time stream,
  they appear in the closest unoccupied space,
  still in their original orientation.
  Determine the closest space randomly if necessary.
\augment{You can augment this power in one or both of the following ways.
\begin{itemize}
  \item For every 2 additional psi dice you spend,
      you can affect a creature of one size category larger.
  \item For every 2 additional psi dice you spend,
      this power can affect an additional target.
      Any additional target cannot be more than
      15 feet from another target of the power.
\end{itemize}}

\DndPowerHeader%
  {Tornado}
  {9th-level Psychokinesis}
  {1 action}
  {120 feet}
  {MB 9, PD 17}
  {Instantaneous}
  You induce the formation of a slender vortex
  of fiercely swirling air.
  When you manifest it,
  a vortex of air visibly and audibly snakes out from your
  outstretched hand.

  If you want to aim the vortex at a specific creature
  you can see in range,
  you can make a psionics attack to strike the creature.
  If you succeed,
  direct contact with the vortex deals 8d6 bludgeoning damage
  to the creature.
  Otherwise,
  you may pick any point you can see in range.
  
  Regardless of whether your psionics attack hits
  (and even if you forgo the attack),
  all creatures
  (including the one possibly damaged by direct contact)
  within a cylinder of radius 40 feet
  and height 100 feet
  are picked up and violently dashed about,
  dealing 17d6 bludgeoning damage to each one.
  Creatures that make a successful Dexterity save
  take half damage.
  
  After being dashed about,
  each creature that was affected finds itself situated
  in a new space 1d4 times 10 feet
  away from its original space in a random direction.
  Walls and other barriers can restrict this relocation;
  in such a case,
  the creature ends up adjacent to the barrier.

\DndPowerHeader%
  {Touchsight}
  {3rd-level Prana Bindu}
  {1 action}
  {Self}
  {MB 3, PD 5}
  {Concentration, up to 1 minute}
  You generate a subtle telekinetic field of mental contact,
  allowing you to `feel' your surroundings even in total darkness
  or when your sight would otherwise be obscured
  by your physical environment.
  Your touchsight field emanates from you out to 60 feet.
  You ignore invisibility, darkness, and concealment,
  though you must have line of sight to a creature or an object
  to discern it.
  
  You do not need to make Wisdom (Perception) checks
  to notice creatures; you can detect and pinpoint all creatures
  within 60 feet.
  In many circumstances, comparing your regular senses
  to what you learn with touchsight is enough to tell you
  the difference between visible, invisible, hiding,
  and concealed creatures.
\augment{For every 2 additional psi dice you spend,
  the radius of your touchsight field increases by 10 feet.}

\DndPowerHeader%
  {Tower of Power}
  {5th-level Voice}
  {1 reaction, which you take when you or an ally is
    targeted by a Voice or mind-affecting power}
  {15 feet}
  {MB 4, PD 9}
  {Concentration, until the start of your next turn}
  You generate a bastion of thought so strong
  that it offers protection to you and all creatures around you,
  improving the self-control of all.
  You and all creatures you choose within 15 feet of you
  can add an extra 2d6 to saving throws against all Voice powers
  and powers that affect one's mind.
  The power lasts until the start of your next turn.
\augment{For every additional psi die you spend,
  this power's duration increases by 1 round.}

\DndPowerHeader%
  {Trace Teleport}
  {4th-level Prescience}
  {1 action}
  {Self}
  {MB 3, PD 7}
  {Instantaneous}
  As for the \power{detect teleportation} power,
  except you can trace the destination of any psionic
  or magical teleportation made by others within
  a 60-foot radius from you
  and that occurred the last minute.

  You know the direction and distance the individuals travelled
  as if you had casually seen the location.
  This power does not grant you any information on the conditions
  at the other end of the trace
  beyond the mental coordinates of the location.
\augment{If you spend 2 additional psi dice,
  this power's range increases to 120 feet.}

\DndPowerHeader%
  {Unrelenting Voice}
  {3rd-level Voice}
  {1 action}
  {Self (30-feet cone)}
  {MB 3, PD 5}
  {Instantaneous}
Your Voice bursts forth from you as tidal wave of raw force,
knocking creatures down.
Any creature that lies within a 30-foot cone centred on yourself
must make a Dexterity saving throw,
taking 6d4 force damage on a failed saving throw or half as much on
a successful roll.
In addition, each target that failed the save
must succeed on a Strength saving throw or be pushed 10 feet back
and knocked prone.
\augment{For every additional psi die you spend,
  this power's damage increases by 1d4.}

\DndPowerHeader%
  {Vigour}
  {1st-level Prana Bindu}
  {1 action}
  {Self}
  {MB 1, PD 1}
  {1 hour}
You suffuse yourself with power,
gaining 5 temporary hit points.
\augment{For every additional psi dice you spend, the number of
  hit points you gain increases by 5.}

  % PK2
\DndPowerHeader%
  {Wall Walker}
  {2nd-level Spacefolding}
  {1 action}
  {Self}
  {MB 2, PD 3}
  {Concentration, up to 1 minute}
  You reverse the direction of gravity in your immediate vicinity,
  allowing you to walk on vertical surfaces
  or even traverse ceilings
  (you need not make any ability checks to traverse these surfaces).
  Because of the need to keep at least one foot in contact
  with the wall or ceiling at all times,
  you cannot jump or use take the dash action,
  and all walls and ceilings walked on in this way count as
  difficult terrain.

\DndPowerHeader%
  {Weapon of Energy}
  {4th-level Psychokinesis}
  {1 action}
  {Touch}
  {MB 4, PD 7}
  {Until the end of your next turn}
  You can manifest this power to
  energise a weapon you are holding.
  The weapon deals an extra 1d8 points of cold,
  lightning, or fire damage
  (as chosen by you at the time of manifestation)
  on a successful hit.

  This power can be manifested on a weapon that
  is magic or otherwise already deals damage the
  aforementioned types of damage,
  and if the weapon already deals the same type of damage
  as the power,
  the effects stack.
  If this power is manifested on a weapon
  already benefiting from the effect of the power,
  the newer manifestation supersedes the older manifestation.