\DndSpellHeader%
    {Logorrhea\label{spl:logorrhea}}
    {2nd-level Enchantment}
    {1 action}
    {Self (60-foot cone)}
    {V, S, M (a papyrus scroll and a vial of ink)}
    {Instantaneous}
You unleash a torrent of meaningless, sibilant sounds targeted
to distract those caught in the blast.
Any creature that can hear you and is
caught in a 60-foot cone centred on yourself must
make an Intelligence saving throw if they are concentrating on
a spell or power. If the target fails the save,
they immediately lose concentration. In addition,
regardless of whether they failed the save or not, a creature
caught in the cone has disadvantage on
Constitution saving throws made to maintain concentration on
a spell or power until the end of their next turn. %
%
\classes{Wizard, Sorcerer, Bard}
\DndSpellHeader%
    {Mental Link\label{spl:mental_link}}
    {3rd-level Abjuration}
    {1 action}
    {Touch}
    {V, S, M (a silver chain worth 50 gp)}
    {1 hour}
You link your mind with a willing creature, cushioning it from
the malign effects of hostile psionics.
While the target is within 60 feet of you, they have resistance
to any damage incurred from a psionic power
or psi-like ability, and may add a d4 to any saving throw
they make to resist a psionic power or psi-like ability.
However, whenever they take psychic damage---regardless
of whether it is caused by a psionic effect
or not---you take half that damage (after applying resistances),
with the target taking the other half.

The spell ends when either you or your target drops to 0 hit points.
You can also dismiss the spell as a free action on your turn.%
%
\classes{Wizard, Cleric}
